---
title: "Data Merge and Clean"
author: "Benjamin W Nelson"
author: "Adam Pettitt"
date: "4/6/2020"
output: html_document
editor_options: 
  chunk_output_type: inline
---
```{r}
packages <- c("magrittr","tidyverse","leaflet","leaflet.extras","car","sjPlot","janitor","corrplot","psych","lmerTest")
if (length(setdiff(packages, rownames(installed.packages()))) > 0) {
  install.packages(setdiff(packages, rownames(installed.packages())))
}
lapply(packages, library, character.only = TRUE)

rm(list=ls())

```

```{r}
qualtrics_data_final <- read.csv("~/Dropbox/COVID-19 Study/Data/qualtrics_final_countries.csv")
#load("~/Dropbox/COVID-19 Study/Data/covid data 4.6.20.RData")

world_data <- read.csv("~/Dropbox/COVID-19 Study/Data/complete_world_data.csv")

world_data$province_state <- as.character(world_data$province_state)
world_data$country_region <- as.character(world_data$country_region)

lockdown_data <- read.csv("~/Dropbox/COVID-19 Study/Data/Lockdown/countryLockdowndates.csv")

```

```{r}
lockdown_data <- clean_names(lockdown_data,"snake")

lockdown_data$lockdown_date <- as.Date(lockdown_data$date, "%d/%m/%y")

lockdown_data$country_region <- gsub("US","United States",lockdown_data$country_region)
lockdown_data$province <- gsub("District of Columbia","District Of Columbia",lockdown_data$province)

lockdown_data$province_state <- as.character(lockdown_data$province)

lockdown_data <- dplyr::select(lockdown_data, -date,-reference,-province,-type)

```


```{r}
world_data$country_region <- gsub("UK","United Kingdom",world_data$country_region)
world_data$country_region <- gsub("US","United States",world_data$country_region)

world_data$date <- as.Date(world_data$date)

world_data <- world_data %>%
  drop_na(date) %>%
  group_by(province_state) %>%
  filter(confirmed > 0) %>%
  mutate(state_diff_days = difftime(date, min(date),units="days")) %>%
  right_join(world_data) %>%
  mutate(state_diff_days = replace_na(state_diff_days, 0)) 

country_level <- world_data %>%
  group_by(date,country_region) %>%
  distinct(confirmed_country)

country_level <- country_level %>%
  drop_na(date) %>%
  group_by(country_region) %>%
  filter(confirmed_country > 0) %>%
  mutate(country_diff_days = difftime(date, min(date),units="days")) %>%
  right_join(country_level) %>%
  mutate(country_diff_days = replace_na(country_diff_days, 0)) 
```

```{r}
world_level <- world_data %>%
  group_by(date) %>%
  distinct(confirmed_world)

world_level <- world_level %>%
  group_by() %>%
  mutate(world_diff_days = difftime(date, min(date),units="days")) 
```

```{r}

world_data$country_region <- as.factor(world_data$country_region)

qualtrics_data_final$date <- as.Date(qualtrics_data_final$start_date)

world_data$date <- as.Date(world_data$date)
world_level$date <- as.Date(world_level$date)
country_level$date <- as.Date(country_level$date)

qualtrics_data_final <- left_join(qualtrics_data_final,world_data,by=c("country_region","province_state","date"))

qualtrics_data_final <- qualtrics_data_final %>%
  dplyr::select(-confirmed_country,-confirmed_world)

qualtrics_data_final <- left_join(qualtrics_data_final,country_level,by=c("country_region","date"))

qualtrics_data_final <- qualtrics_data_final %>% 
  left_join(lockdown_data,by=c("country_region","province_state")) 

lockdown_data <- lockdown_data %>%
  dplyr::filter(province_state == "") %>%
  dplyr::select(-province_state) %>%
  dplyr::rename(lockdown_date.x = lockdown_date)

qualtrics_data_final <- qualtrics_data_final %>%
  left_join(lockdown_data,by=c("country_region")) %>%
  mutate(lockdown_date = coalesce(lockdown_date,lockdown_date.x)) %>%
  dplyr::select(-lockdown_date.x)

update_states <- tibble(province_state = c("District Of Columbia","Georgia","South Carolina","Wyoming"), lockdown_date.x = c("2020-04-01","2020-04-03","2020-04-07","2020-03-28")) 

update_states$lockdown_date.x <- as.Date(update_states$lockdown_date.x)

qualtrics_data_final <- qualtrics_data_final %>%
  left_join(update_states,by=c("province_state")) %>%
  mutate(lockdown_date = coalesce(lockdown_date,lockdown_date.x)) %>%
  dplyr::select(-lockdown_date.x)

qualtrics_data_final %>%
  dplyr::select(country_region,province_state,lockdown_date)

qualtrics_data_final <- left_join(qualtrics_data_final,world_level,by=c("date"))



qualtrics_data_final <- qualtrics_data_final %>%
  drop_na(date) %>%
  group_by(country_region,province_state) %>%
  mutate(days_since_lockdown = difftime(date, lockdown_date,units="days")) 

#test <- qualtrics_data_final %>%
  #mutate(days_since_lockdown =  ifelse(days_since_lockdown < 0 | is.na(days_since_lockdown), 0,days_since_lockdown)) %>%
  #select(country_region,province_state,days_since_lockdown,lockdown_date,date)

qualtrics_data_final$confirmed_log <- log(qualtrics_data_final$confirmed)
qualtrics_data_final$confirmed_country_log <- log(qualtrics_data_final$confirmed_country)
qualtrics_data_final$confirmed_world_log <- log(qualtrics_data_final$confirmed_world)

data_final <- qualtrics_data_final

data_final <- data_final %>% 
  dplyr::select(-X.x)

str(data_final$covid_concern)
```
#Data Cleaning

##Remove Columns that Won't Be Used
```{r}
variables_remove <- names(data_final) %in% c("finished",
                                             "sig_req",
                                             "sig_pic",
                                             "sig_size",
                                             "sig_type",
                                             "email") # Identify variables you want to remove

data_final <- data_final[!variables_remove]
data_final <- data_final %>% 
  dplyr::select(-X.y)
```

##Numeric
```{r}
# Change variables to numeric
cols_num <- c("phq_q1", 
              "phq_q2",
              "gad_q1",
              "gad_q2")
data_final[, cols_num] %<>%
  lapply(function(x) as.numeric(as.character(x)))
```

##Clean PHQ
```{r}
data_final$phq_total <- data_final$phq_q1 + data_final$phq_q2
```

##Clean GAD
```{r}
data_final$gad_total <- data_final$gad_q1 + data_final$gad_q2
```

##Clean COVID Concern
```{r}
str(data_final$covid_concern)

data_final$covid_concern <- factor(data_final$covid_concern,
                                             levels = c(0, 1, 2, 3, 4),
                                             labels = c("Not at all concerned", 
                                                        "A little concerned",
                                                        "Moderately concerned",
                                                        "Very concerned",
                                                        "Extremely concerned"))

data_final$covid_concern_integer <- as.integer(data_final$covid_concern)
describe(data_final$covid_concern_integer)

covid_concern <- data_final %>%
  group_by(covid_concern) %>%
  count() %>%
  mutate(percentage = (n/length(data_final$covid_concern))*100) %>% 
  arrange(desc(n)) %>% 
  drop_na()


covid_concern$covid_concern <- factor(covid_concern$covid_concern, levels = covid_concern$covid_concern[order(covid_concern$n)])
covid_concern$covid_concern  # notice the changed order of factor levels


covid_concern_plot <- covid_concern %>%
  ggplot( aes(x=covid_concern, y=n)) +
  geom_bar(stat="identity", fill="#D95F02FF", alpha=.6, width=.4) +
  coord_flip() +
  xlab("") +
  theme_bw() + theme(axis.ticks = element_line(colour = "black"), 
                     panel.grid.major = element_line(colour = "black", 
                                                     linetype = "blank"), panel.grid.minor = element_line(colour = "black", 
                                                                                                          linetype = "blank"), axis.title = element_text(size = 12), 
                     axis.text = element_text(size = 12, colour = "black"), 
                     axis.text.x = element_text(colour = "black"), 
                     axis.text.y = element_text(colour = "black")) +
  labs(x = NULL, y = "Number of Participants") +
  theme(axis.line = element_line(linetype = "solid"), 
        axis.ticks = element_line(size = 1)) + 
  theme(panel.grid.major = element_line(size = 0.1, 
                                        linetype = "solid")) + 
  labs(title = "COVID-19 Concern")
covid_concern_plot
```


##Clean Race
```{r}
data_final <-  data_final %>%
  mutate(race_cleaned = ifelse(race %in% '1', "1",
                               ifelse(race %in% '2', "2",
                                      ifelse(race %in% '3', "3",
                                             ifelse(race %in% '4', "4",
                                                    ifelse(race %in% '5', "5",
                                                           ifelse(race %in% '6', "6",
                                                                  ifelse(race %in% '7', "7",
                                                                         ifelse(race %in% '8', "7", "8"
                                                                         )))))))))
#The last line changes "prefer to self-describe" to "race not listed" and then makes any participant that put more than one race as 8

data_final$race_cleaned <- factor(data_final$race_cleaned,
                                            levels = c(1, 2, 3, 4, 5, 6, 7, 8), 
                                            labels = c("White/Caucasian", 
                                                       "Black/African-American",
                                                       "Latino/Latina/Latinx",
                                                       "Asian",
                                                       "Pacific Islander/Native Hawaiian",
                                                       "Native American/Alaskan Native",
                                                       "Race not listed",
                                                       "More than one race"))



library(forcats)

race <- data_final %>%
  group_by(race_cleaned) %>%
  count() %>%
  mutate(percentage = (n/length(data_final$race_cleaned))*100) %>% 
  arrange(desc(n))


race$race_cleaned <- factor(race$race_cleaned, levels = race$race_cleaned[order(race$n)])
race$race_cleaned  # notice the changed order of factor levels


race_plot <- race %>%
  ggplot( aes(x=race_cleaned, y=n)) +
    geom_bar(stat="identity", fill="#1B9E77FF", alpha=.6, width=.4) +
    coord_flip() +
    xlab("") +
    theme_bw() + theme(axis.ticks = element_line(colour = "black"), 
    panel.grid.major = element_line(colour = "black", 
        linetype = "blank"), panel.grid.minor = element_line(colour = "black", 
        linetype = "blank"), axis.title = element_text(size = 12), 
    axis.text = element_text(size = 12, colour = "black"), 
    axis.text.x = element_text(colour = "black"), 
    axis.text.y = element_text(colour = "black")) +
  labs(x = NULL, y = "Number of Participants") +
  theme(axis.line = element_line(linetype = "solid"), 
    axis.ticks = element_line(size = 1)) + 
  theme(panel.grid.major = element_line(size = 0.1, 
    linetype = "solid")) + 
    labs(title = "Race")
race_plot


```

##Clean Ethnicity
```{r}
data_final$ethnicity_cleaned <- factor(data_final$ethnicity,
                                                 levels = c(1, 2, 3),
                                                 labels = c("Hispanic", 
                                                            "Non-Hispanic",
                                                            "Prefer not to answer"))


ethnicity <- data_final %>%
  group_by(ethnicity_cleaned) %>%
  count() %>%
  mutate(percentage = (n/length(data_final$ethnicity_cleaned))*100) %>% 
  arrange(desc(n)) %>% 
  drop_na()


ethnicity$ethnicity_cleaned <- factor(ethnicity$ethnicity_cleaned, levels = ethnicity$ethnicity_cleaned[order(ethnicity$n)])
ethnicity$ethnicity_cleaned  # notice the changed order of factor levels


ethnicity_plot <- ethnicity %>%
  ggplot( aes(x=ethnicity_cleaned, y=n)) +
  geom_bar(stat="identity", fill="#1B9E77FF", alpha=.6, width=.4) +
  coord_flip() +
  xlab("") +
  theme_bw() + theme(axis.ticks = element_line(colour = "black"), 
                     panel.grid.major = element_line(colour = "black", 
                                                     linetype = "blank"), panel.grid.minor = element_line(colour = "black", 
                                                                                                          linetype = "blank"), axis.title = element_text(size = 12), 
                     axis.text = element_text(size = 12, colour = "black"), 
                     axis.text.x = element_text(colour = "black"), 
                     axis.text.y = element_text(colour = "black")) +
  labs(x = NULL, y = "Number of Participants") +
  theme(axis.line = element_line(linetype = "solid"), 
        axis.ticks = element_line(size = 1)) + 
  theme(panel.grid.major = element_line(size = 0.1, 
                                        linetype = "solid")) + 
    labs(title = "Ethnicity")
ethnicity_plot


```

##Clean Gender
```{r}
data_final$gender_cleaned <- factor(data_final$gender,
                                              levels = c(0, 1, 2, 3, 4),
                                              labels = c("Male/Man", 
                                                         "Female/Woman",
                                                         "Nonbinary",
                                                         "Prefer to self describe",
                                                         "Prefer not to answer"))

gender <- data_final %>%
  group_by(gender_cleaned) %>%
  count() %>%
  mutate(percentage = (n/length(data_final$gender_cleaned))*100) %>% 
  arrange(desc(n)) %>% 
  drop_na()


gender$gender_cleaned <- factor(gender$gender_cleaned, levels = gender$gender_cleaned[order(gender$n)])
gender$gender_cleaned  # notice the changed order of factor levels


gender_plot <- gender %>%
  ggplot( aes(x=gender_cleaned, y=n)) +
  geom_bar(stat="identity", fill="#1B9E77FF", alpha=.6, width=.4) +
  coord_flip() +
  xlab("") +
  theme_bw() + theme(axis.ticks = element_line(colour = "black"), 
                     panel.grid.major = element_line(colour = "black", 
                                                     linetype = "blank"), panel.grid.minor = element_line(colour = "black", 
                                                                                                          linetype = "blank"), axis.title = element_text(size = 12), 
                     axis.text = element_text(size = 12, colour = "black"), 
                     axis.text.x = element_text(colour = "black"), 
                     axis.text.y = element_text(colour = "black")) +
  labs(x = NULL, y = "Number of Participants") +
  theme(axis.line = element_line(linetype = "solid"), 
        axis.ticks = element_line(size = 1)) + 
  theme(panel.grid.major = element_line(size = 0.1, 
                                        linetype = "solid")) + 
    labs(title = "Gender")
gender_plot
```

##Clean Flu Sxs
```{r}
data_final$flu_sxs_personal <- factor(data_final$flu_sxs_personal,
                                              levels = c(0, 1),
                                              labels = c("No", 
                                                         "Yes"))

flu_personal <- data_final %>%
  group_by(flu_sxs_personal) %>%
  count() %>%
  arrange(desc(n)) %>% 
  drop_na()

flu_personal_plot <- flu_personal %>%
  ggplot( aes(x=flu_sxs_personal, y=n)) +
  geom_bar(stat="identity", fill="#f68060", alpha=.6, width=.4) +
  coord_flip() +
  xlab("") +
  theme_bw() + theme(axis.ticks = element_line(colour = "black"), 
                     panel.grid.major = element_line(colour = "black", 
                                                     linetype = "blank"), panel.grid.minor = element_line(colour = "black", 
                                                                                                          linetype = "blank"), axis.title = element_text(size = 12), 
                     axis.text = element_text(size = 12, colour = "black"), 
                     axis.text.x = element_text(colour = "black"), 
                     axis.text.y = element_text(colour = "black")) +
  labs(x = NULL, y = "Number of Participants") +
  theme(axis.line = element_line(linetype = "solid"), 
        axis.ticks = element_line(size = 1)) + 
  theme(panel.grid.major = element_line(size = 0.1, 
                                        linetype = "solid"))+
  labs(title = "Any Personal Flu Symptoms?")
flu_personal_plot

#####################


data_final$flu_sxs_other <- factor(data_final$flu_sxs_other,
                                              levels = c(0, 1),
                                              labels = c("No", 
                                                         "Yes"))

flu_other <- data_final %>%
  group_by(flu_sxs_other) %>%
  count() %>%
  arrange(desc(n)) %>% 
  drop_na()

flu_other_plot <- flu_other %>%
  ggplot( aes(x=flu_sxs_other, y=n)) +
  geom_bar(stat="identity", fill="#f68060", alpha=.6, width=.4) +
  coord_flip() +
  xlab("") +
  theme_bw() + theme(axis.ticks = element_line(colour = "black"), 
                     panel.grid.major = element_line(colour = "black", 
                                                     linetype = "blank"), panel.grid.minor = element_line(colour = "black", 
                                                                                                          linetype = "blank"), axis.title = element_text(size = 12), 
                     axis.text = element_text(size = 12, colour = "black"), 
                     axis.text.x = element_text(colour = "black"), 
                     axis.text.y = element_text(colour = "black")) +
  labs(x = NULL, y = "Number of Participants") +
  theme(axis.line = element_line(linetype = "solid"), 
        axis.ticks = element_line(size = 1)) + 
  theme(panel.grid.major = element_line(size = 0.1, 
                                        linetype = "solid")) + 
  labs(title = "Know Other's With Flu Symptoms?")
flu_other_plot

#############################

##For specific measures change NA to 0

data_final$flu_sxs_other_number[is.na(data_final$flu_sxs_other_number)] <- 0

data_final$hospitalized_number[is.na(data_final$hospitalized_number)] <- 0
#describe(data_final$hospitalized_number)

data_final$passed_away_number[is.na(data_final$passed_away_number)] <- 0
#describe(data_final$passed_away_number) #One participant entered value of 34646762600, replace with NA

data_final <- data_final %>% 
  naniar::replace_with_na(replace = list(passed_away_number = 34646762600))

describe(data_final$passed_away_number)



#Clean Type of Symptoms
#Use this code to create separate columns for each symptom
#data <- data %>%
  #mutate(
    #share_keyboard = ifelse(grepl("keyboard", data_types_share), "yes", "no"),
    #share_geolocation = ifelse(grepl("Geolocation", data_types_share), "yes", "no"),
    #share_selfies = ifelse(grepl("Selfies", data_types_share), "yes", "no"),
    #share_voice = ifelse(grepl("Voice", data_types_share), "yes", "no"),
    #share_movement = ifelse(grepl("Movement", data_types_share), "yes", "no")
#  )
```

##Clean COVID Test
```{r}
#Note 4 and 6 are the same, because an additional option was entered to qualtrics
data_final$covid_test <- factor(data_final$covid_test,
                                              levels = c(1, 2, 3, 4, 5, 6),
                                              labels = c("Yes, positive", 
                                                         "Yes, negative",
                                                         "Yes, waiting for results",
                                                         "No, did not try",
                                                         "No, could not get test",
                                                         "No, did not try"))

covid_test <- data_final %>%
  group_by(covid_test) %>%
  count() %>%
  mutate(percentage = (n/length(data_final$covid_test))*100) %>% 
  arrange(desc(n)) %>% 
  drop_na()


covid_test$covid_test <- factor(covid_test$covid_test, levels = covid_test$covid_test[order(covid_test$n)])
covid_test$covid_test  # notice the changed order of factor levels


covid_test_plot <- covid_test %>%
  ggplot( aes(x=covid_test, y=n)) +
  geom_bar(stat="identity", fill="#D95F02FF", alpha=.6, width=.4) +
  coord_flip() +
  xlab("") +
  theme_bw() + theme(axis.ticks = element_line(colour = "black"), 
                     panel.grid.major = element_line(colour = "black", 
                                                     linetype = "blank"), panel.grid.minor = element_line(colour = "black", 
                                                                                                          linetype = "blank"), axis.title = element_text(size = 12), 
                     axis.text = element_text(size = 12, colour = "black"), 
                     axis.text.x = element_text(colour = "black"), 
                     axis.text.y = element_text(colour = "black")) +
  labs(x = NULL, y = "Number of Participants") +
  theme(axis.line = element_line(linetype = "solid"), 
        axis.ticks = element_line(size = 1)) + 
  theme(panel.grid.major = element_line(size = 0.1, 
                                        linetype = "solid")) + 
  labs(title = "Received COVID-19 Testing?")
covid_test_plot


```

##Clean Hopsitalized
```{r}
data_final$hospitalized <- factor(data_final$hospitalized,
                                              levels = c(0, 1),
                                              labels = c("No", 
                                                         "Yes"))

hospitalized <- data_final %>%
  group_by(hospitalized) %>%
  count() %>%
  mutate(percentage = (n/length(data_final$hospitalized))*100) %>% 
  arrange(desc(n)) %>% 
  drop_na()


hospitalized$hospitalized <- factor(hospitalized$hospitalized, levels = hospitalized$hospitalized[order(hospitalized$n)])
hospitalized$hospitalized  # notice the changed order of factor levels


hospitalized_plot <- hospitalized %>%
  ggplot( aes(x=hospitalized, y=n)) +
  geom_bar(stat="identity", fill="#D95F02FF", alpha=.6, width=.4) +
  coord_flip() +
  xlab("") +
  theme_bw() + theme(axis.ticks = element_line(colour = "black"), 
                     panel.grid.major = element_line(colour = "black", 
                                                     linetype = "blank"), panel.grid.minor = element_line(colour = "black", 
                                                                                                          linetype = "blank"), axis.title = element_text(size = 12), 
                     axis.text = element_text(size = 12, colour = "black"), 
                     axis.text.x = element_text(colour = "black"), 
                     axis.text.y = element_text(colour = "black")) +
  labs(x = NULL, y = "Number of Participants") +
  theme(axis.line = element_line(linetype = "solid"), 
        axis.ticks = element_line(size = 1)) + 
  theme(panel.grid.major = element_line(size = 0.1, 
                                        linetype = "solid")) + 
  labs(title = "Hospitalized due to COVID-19?")
hospitalized_plot

```

##Clean Passed Away
```{r}
data_final$passed_away <- factor(data_final$passed_away,
                                              levels = c(0, 1),
                                              labels = c("No", 
                                                         "Yes"))

passed_away <- data_final %>%
  group_by(passed_away) %>%
  count() %>%
  mutate(percentage = (n/length(data_final$passed_away))*100) %>% 
  arrange(desc(n)) %>% 
  drop_na()


passed_away$passed_away <- factor(passed_away$passed_away, levels = passed_away$passed_away[order(passed_away$n)])
passed_away$passed_away  # notice the changed order of factor levels


passed_away_plot <- passed_away %>%
  ggplot( aes(x=passed_away, y=n)) +
  geom_bar(stat="identity", fill="#D95F02FF", alpha=.6, width=.4) +
  coord_flip() +
  xlab("") +
  theme_bw() + theme(axis.ticks = element_line(colour = "black"), 
                     panel.grid.major = element_line(colour = "black", 
                                                     linetype = "blank"), panel.grid.minor = element_line(colour = "black", 
                                                                                                          linetype = "blank"), axis.title = element_text(size = 12), 
                     axis.text = element_text(size = 12, colour = "black"), 
                     axis.text.x = element_text(colour = "black"), 
                     axis.text.y = element_text(colour = "black")) +
  labs(x = NULL, y = "Number of Participants") +
  theme(axis.line = element_line(linetype = "solid"), 
        axis.ticks = element_line(size = 1)) + 
  theme(panel.grid.major = element_line(size = 0.1, 
                                        linetype = "solid")) + 
  labs(title = "Personally know persons passed away?")
passed_away_plot
```

##Clean Lifestyle Changes
```{r}
data_final$lifestyle_changes <- factor(data_final$lifestyle_changes,
                                              levels = c(0, 1),
                                              labels = c("No", 
                                                         "Yes"))

lifestyle_changes <- data_final %>%
  group_by(lifestyle_changes) %>%
  count() %>%
  mutate(percentage = (n/length(data_final$lifestyle_changes))*100) %>% 
  arrange(desc(n)) %>% 
  drop_na()


lifestyle_changes$lifestyle_changes <- factor(lifestyle_changes$lifestyle_changes, levels = lifestyle_changes$lifestyle_changes[order(lifestyle_changes$n)])
lifestyle_changes$lifestyle_changes  # notice the changed order of factor levels


lifestyle_changes_plot <- lifestyle_changes %>%
  ggplot( aes(x=lifestyle_changes, y=n)) +
  geom_bar(stat="identity", fill="#66A61EFF", alpha=.6, width=.4) +
  coord_flip() +
  xlab("") +
  theme_bw() + theme(axis.ticks = element_line(colour = "black"), 
                     panel.grid.major = element_line(colour = "black", 
                                                     linetype = "blank"), panel.grid.minor = element_line(colour = "black", 
                                                                                                          linetype = "blank"), axis.title = element_text(size = 12), 
                     axis.text = element_text(size = 12, colour = "black"), 
                     axis.text.x = element_text(colour = "black"), 
                     axis.text.y = element_text(colour = "black")) +
  labs(x = NULL, y = "Number of Participants") +
  theme(axis.line = element_line(linetype = "solid"), 
        axis.ticks = element_line(size = 1)) + 
  theme(panel.grid.major = element_line(size = 0.1, 
                                        linetype = "solid")) + 
  labs(title = "Made Changes to Lifestyle?")
lifestyle_changes_plot

```

##Clean Quarantine
```{r}
data_final$self_quarantine <- factor(data_final$self_quarantine,
                                              levels = c(0, 1, 2, 3),
                                              labels = c("None of the time", 
                                                         "Some of the time",
                                                         "Most of the time",
                                                         "All of the time"))

self_quarantine <- data_final %>%
  group_by(self_quarantine) %>%
  count() %>%
  mutate(percentage = (n/length(data_final$self_quarantine))*100) %>% 
  arrange(desc(n)) %>% 
  drop_na()


self_quarantine$self_quarantine <- factor(self_quarantine$self_quarantine, levels = self_quarantine$self_quarantine[order(self_quarantine$n)])
self_quarantine$self_quarantine  # notice the changed order of factor levels


quarantine_plot <- self_quarantine %>%
  ggplot( aes(x=self_quarantine, y=n)) +
  geom_bar(stat="identity", fill="#66A61EFF", alpha=.6, width=.4) +
  coord_flip() +
  xlab("") +
  theme_bw() + theme(axis.ticks = element_line(colour = "black"), 
                     panel.grid.major = element_line(colour = "black", 
                                                     linetype = "blank"), panel.grid.minor = element_line(colour = "black", 
                                                                                                          linetype = "blank"), axis.title = element_text(size = 12), 
                     axis.text = element_text(size = 12, colour = "black"), 
                     axis.text.x = element_text(colour = "black"), 
                     axis.text.y = element_text(colour = "black")) +
  labs(x = NULL, y = "Number of Participants") +
  theme(axis.line = element_line(linetype = "solid"), 
        axis.ticks = element_line(size = 1)) + 
  theme(panel.grid.major = element_line(size = 0.1, 
                                        linetype = "solid")) + 
  labs(title = "Degree of Self-Quarantine")
quarantine_plot
```

##Clean Job
```{r}
data_final$job_lost <- factor(data_final$job_lost,
                                              levels = c(0, 1),
                                              labels = c("No", 
                                                         "Yes"))

job_lost <- data_final %>%
  group_by(job_lost) %>%
  count() %>%
  mutate(percentage = (n/length(data_final$job_lost))*100) %>% 
  arrange(desc(n)) %>% 
  drop_na()


job_lost$job_lost <- factor(job_lost$job_lost, levels = job_lost$job_lost[order(job_lost$n)])
job_lost$job_lost  # notice the changed order of factor levels


job_lost_plot <- job_lost %>%
  ggplot( aes(x=job_lost, y=n)) +
  geom_bar(stat="identity", fill="#7570B3FF", alpha=.6, width=.4) +
  coord_flip() +
  xlab("") +
  theme_bw() + theme(axis.ticks = element_line(colour = "black"), 
                     panel.grid.major = element_line(colour = "black", 
                                                     linetype = "blank"), panel.grid.minor = element_line(colour = "black", 
                                                                                                          linetype = "blank"), axis.title = element_text(size = 12), 
                     axis.text = element_text(size = 12, colour = "black"), 
                     axis.text.x = element_text(colour = "black"), 
                     axis.text.y = element_text(colour = "black")) +
  labs(x = NULL, y = "Number of Participants") +
  theme(axis.line = element_line(linetype = "solid"), 
        axis.ticks = element_line(size = 1)) + 
  theme(panel.grid.major = element_line(size = 0.1, 
                                        linetype = "solid")) + 
  labs(title = "Job Loss")
job_lost_plot

#########################
data_final$job_unable_work <- factor(data_final$job_unable_work,
                                              levels = c(0, 1),
                                              labels = c("No", 
                                                         "Yes"))

data_final %>%
  group_by(job_unable_work) %>%
  count() %>%
  arrange(desc(n))

#########################
data_final$income_lost <- factor(data_final$income_lost,
                                              levels = c(0, 1),
                                              labels = c("No", 
                                                         "Yes"))

income_lost <- data_final %>%
  group_by(income_lost) %>%
  count() %>%
  mutate(percentage = (n/length(data_final$income_lost))*100) %>% 
  arrange(desc(n)) %>% 
  drop_na()


income_lost$income_lost <- factor(income_lost$income_lost, levels = income_lost$income_lost[order(income_lost$n)])
income_lost$income_lost  # notice the changed order of factor levels


income_lost_plot <- income_lost %>%
  ggplot( aes(x=income_lost, y=n)) +
  geom_bar(stat="identity", fill="#7570B3FF", alpha=.6, width=.4) +
  coord_flip() +
  xlab("") +
  theme_bw() + theme(axis.ticks = element_line(colour = "black"), 
                     panel.grid.major = element_line(colour = "black", 
                                                     linetype = "blank"), panel.grid.minor = element_line(colour = "black", 
                                                                                                          linetype = "blank"), axis.title = element_text(size = 12), 
                     axis.text = element_text(size = 12, colour = "black"), 
                     axis.text.x = element_text(colour = "black"), 
                     axis.text.y = element_text(colour = "black")) +
  labs(x = NULL, y = "Number of Participants") +
  theme(axis.line = element_line(linetype = "solid"), 
        axis.ticks = element_line(size = 1)) + 
  theme(panel.grid.major = element_line(size = 0.1, 
                                        linetype = "solid")) + 
  labs(title = "Have you lost income?")
income_lost_plot


#########################
data_final$money_situation <- factor(data_final$money_situation,
                                              levels = c(1, 2, 3, 4),
                                              labels = c("Comfortable with extra", 
                                                         "Enough, but no extra",
                                                         "Have to cut back",
                                                         "Cannot make ends meet"))

money_situation <- data_final %>%
  group_by(money_situation) %>%
  count() %>%
  mutate(percentage = (n/length(data_final$money_situation))*100) %>% 
  arrange(desc(n)) %>% 
  drop_na()


money_situation$money_situation <- factor(money_situation$money_situation, levels = money_situation$money_situation[order(money_situation$n)])
money_situation$money_situation  # notice the changed order of factor levels


money_situation_plot <- money_situation %>%
  ggplot( aes(x=money_situation, y=n)) +
  geom_bar(stat="identity", fill="#7570B3FF", alpha=.6, width=.4) +
  coord_flip() +
  xlab("") +
  theme_bw() + theme(axis.ticks = element_line(colour = "black"), 
                     panel.grid.major = element_line(colour = "black", 
                                                     linetype = "blank"), panel.grid.minor = element_line(colour = "black", 
                                                                                                          linetype = "blank"), axis.title = element_text(size = 12), 
                     axis.text = element_text(size = 12, colour = "black"), 
                     axis.text.x = element_text(colour = "black"), 
                     axis.text.y = element_text(colour = "black")) +
  labs(x = NULL, y = "Number of Participants") +
  theme(axis.line = element_line(linetype = "solid"), 
        axis.ticks = element_line(size = 1)) + 
  theme(panel.grid.major = element_line(size = 0.1, 
                                        linetype = "solid")) + 
  labs(title = "Money Situation")
money_situation_plot


#########################
data_final$food_security <- factor(data_final$food_security,
                                              levels = c(1, 2, 3),
                                              labels = c("Never true", 
                                                         "Sometimes true",
                                                         "Often true"))

food_security <- data_final %>%
  group_by(food_security) %>%
  count() %>%
  mutate(percentage = (n/length(data_final$food_security))*100) %>% 
  arrange(desc(n)) %>% 
  drop_na()


food_security$food_security <- factor(food_security$food_security, levels = food_security$food_security[order(food_security$n)])
food_security$food_security  # notice the changed order of factor levels


food_security_plot <- food_security %>%
  ggplot( aes(x=food_security, y=n)) +
  geom_bar(stat="identity", fill="#7570B3FF", alpha=.6, width=.4) +
  coord_flip() +
  xlab("") +
  theme_bw() + theme(axis.ticks = element_line(colour = "black"), 
                     panel.grid.major = element_line(colour = "black", 
                                                     linetype = "blank"), panel.grid.minor = element_line(colour = "black", 
                                                                                                          linetype = "blank"), axis.title = element_text(size = 12), 
                     axis.text = element_text(size = 12, colour = "black"), 
                     axis.text.x = element_text(colour = "black"), 
                     axis.text.y = element_text(colour = "black")) +
  labs(x = NULL, y = "Number of Participants") +
  theme(axis.line = element_line(linetype = "solid"), 
        axis.ticks = element_line(size = 1)) + 
  theme(panel.grid.major = element_line(size = 0.1, 
                                        linetype = "solid")) + 
  labs(title = "During past 12 months, food we bought ran out and didn't have money to get
more")
food_security_plot


#########################
data_final$income <- factor(data_final$income,
                                              levels = c(1, 2, 3, 4, 5, 6, 7, 8, 9),
                                              labels = c("Less than $4,999", 
                                                         "$5,000-$9,999",
                                                         "$10,000-$19,999",
                                                         "$20,000-$49,999",
                                                         "$50,000-$99,999",
                                                         "$100,000-$149,999",
                                                         "$150,000+",
                                                         "Don’t know",
                                                         "Prefer not to answer"))

income <- data_final %>%
  group_by(income) %>%
  count() %>%
  mutate(percentage = (n/length(data_final$income))*100) %>% 
  arrange(desc(n)) %>% 
  drop_na()


income$income <- factor(income$income, levels = income$income[order(income$n)])
income$income  # notice the changed order of factor levels


income_plot <- income %>%
  ggplot( aes(x=income, y=n)) +
  geom_bar(stat="identity", fill="#1B9E77FF", alpha=.6, width=.4) +
  coord_flip() +
  xlab("") +
  theme_bw() + theme(axis.ticks = element_line(colour = "black"), 
                     panel.grid.major = element_line(colour = "black", 
                                                     linetype = "blank"), panel.grid.minor = element_line(colour = "black", 
                                                                                                          linetype = "blank"), axis.title = element_text(size = 12), 
                     axis.text = element_text(size = 12, colour = "black"), 
                     axis.text.x = element_text(colour = "black"), 
                     axis.text.y = element_text(colour = "black")) +
  labs(x = NULL, y = "Number of Participants") +
  theme(axis.line = element_line(linetype = "solid"), 
        axis.ticks = element_line(size = 1)) + 
  theme(panel.grid.major = element_line(size = 0.1, 
                                        linetype = "solid")) + 
  labs(title = "Yearly Income")
income_plot

```

##Clean Education
```{r}
data_final$education <- factor(data_final$education,
                                              levels = c(1, 2, 3, 4, 5, 6, 7),
                                              labels = c("Some high school", 
                                                         "High school diploma/GED",
                                                         "Vocational/Technical school (2 years)",
                                                         "Some college",
                                                         "College graduate (4 years)",
                                                         "Graduate or Professional degree",
                                                         "Other"))

education <- data_final %>%
  group_by(education) %>%
  count() %>%
  mutate(percentage = (n/length(data_final$education))*100) %>% 
  arrange(desc(n)) %>% 
  drop_na()


education$education <- factor(education$education, levels = education$education[order(education$n)])
education$education  # notice the changed order of factor levels


education_plot <- education %>%
  ggplot( aes(x=education, y=n)) +
  geom_bar(stat="identity", fill="#1B9E77FF", alpha=.6, width=.4) +
  coord_flip() +
  xlab("") +
  theme_bw() + theme(axis.ticks = element_line(colour = "black"), 
                     panel.grid.major = element_line(colour = "black", 
                                                     linetype = "blank"), panel.grid.minor = element_line(colour = "black", 
                                                                                                          linetype = "blank"), axis.title = element_text(size = 12), 
                     axis.text = element_text(size = 12, colour = "black"), 
                     axis.text.x = element_text(colour = "black"), 
                     axis.text.y = element_text(colour = "black")) +
  labs(x = NULL, y = "Number of Participants") +
  theme(axis.line = element_line(linetype = "solid"), 
        axis.ticks = element_line(size = 1)) + 
  theme(panel.grid.major = element_line(size = 0.1, 
                                        linetype = "solid")) + 
  labs(title = "Education")
education_plot

```

##Clean Disability
```{r}
data_final <-  data_final %>%
  mutate(disability = ifelse(disability %in% '1', "1",
                               ifelse(disability %in% '2', "2",
                                      ifelse(disability %in% '3', "3",
                                             ifelse(disability %in% '4', "4", "5"
                                                                         )))))
#The last line makes any participant that put more than one disability a 5

data_final$disability <- factor(data_final$disability,
                                            levels = c(1, 2, 3, 4, 5),
                                            labels = c("Physical Disability/Disabilities", 
                                                       "Mental Disability/Disabilities",
                                                       "No Disability",
                                                       "Prefer not to answer",
                                                       "Both Physical and Mental Disabilities"))

data_final %>%
  group_by(disability) %>%
  count() %>%
  arrange(desc(n))
```

##Clean Political Orientation
```{r}
data_final$political_orientation <- factor(data_final$political_orientation,
                                              levels = c(1, 2, 3, 4, 5),
                                              labels = c("Very Conservative", 
                                                         "Conservative",
                                                         "Moderate",
                                                         "Liberal",
                                                         "Very Liberal"))

political_orientation <- data_final %>%
  group_by(political_orientation) %>%
  count() %>%
  mutate(percentage = (n/length(data_final$political_orientation))*100) %>% 
  arrange(desc(n)) %>% 
  drop_na()


political_orientation$political_orientation <- factor(political_orientation$political_orientation, levels = political_orientation$political_orientation[order(political_orientation$n)])
political_orientation$political_orientation  # notice the changed order of factor levels


political_plot <- political_orientation %>%
  ggplot( aes(x=political_orientation, y=n)) +
  geom_bar(stat="identity", fill="#1B9E77FF", alpha=.6, width=.4) +
  coord_flip() +
  xlab("") +
  theme_bw() + theme(axis.ticks = element_line(colour = "black"), 
                     panel.grid.major = element_line(colour = "black", 
                                                     linetype = "blank"), panel.grid.minor = element_line(colour = "black", 
                                                                                                          linetype = "blank"), axis.title = element_text(size = 12), 
                     axis.text = element_text(size = 12, colour = "black"), 
                     axis.text.x = element_text(colour = "black"), 
                     axis.text.y = element_text(colour = "black")) +
  labs(x = NULL, y = "Number of Participants") +
  theme(axis.line = element_line(linetype = "solid"), 
        axis.ticks = element_line(size = 1)) + 
  theme(panel.grid.major = element_line(size = 0.1, 
                                        linetype = "solid")) + 
  labs(title = "Political Orientation")
political_plot

```

##Clean Occupation
```{r}
data_final <-  data_final %>%
  mutate(occupation = ifelse(occupation %in% '1', "1",
                      ifelse(occupation %in% '2', "2",
                      ifelse(occupation %in% '3', "3",
                      ifelse(occupation %in% '4', "4",
                      ifelse(occupation %in% '5', "5",
                      ifelse(occupation %in% '6', "6",
                      ifelse(occupation %in% '7', "7",
                      ifelse(occupation %in% '8', "8",
                      ifelse(occupation %in% '9', "9",
                      ifelse(occupation %in% '10', "10",
                      ifelse(occupation %in% '11', "11",
                      ifelse(occupation %in% '12', "12",
                      ifelse(occupation %in% '13', "13",
                      ifelse(occupation %in% '14', "14",
                      ifelse(occupation %in% '15', "15",
                      ifelse(occupation %in% '16', "16",
                      ifelse(occupation %in% '17', "17",
                      ifelse(occupation %in% '18', "18",
                      ifelse(occupation %in% '19', "19",
                      ifelse(occupation %in% '20', "20",
                      ifelse(occupation %in% '21', "21",
                      ifelse(occupation %in% '22', "22",
                      ifelse(occupation %in% '23', "23",
                      ifelse(occupation %in% '24', "24",
                      ifelse(occupation %in% '25', "25", "26"
                                                                         ))))))))))))))))))))))))))
#The last line makes any participant that put more than one occupation
data_final$occupation <- as.numeric(data_final$occupation)

data_final$occupation <- factor(data_final$occupation,
                                            levels = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 16, 17, 18, 19, 20, 21, 22, 23, 24, 25, 26),
                                            labels = c("Management", 
                                                       "Business/Financial",
                                                       "Computer/Mathematical",
                                                       "Architecture/Engineering",
                                                       "Life/Physical/Social Science",
                                                       "Community/Social Service ",
                                                       "Legal ",
                                                       "Teaching/Library",
                                                       "Arts/Design/Sports/Media ",
                                                       "Healthcare Practice/Technical",
                                                       "Healthcare/Support",
                                                       "Protective Service",
                                                       "Food Preparation/Serving",
                                                       "Cleaning/Maintenance",
                                                       "Personal Care/Service",
                                                       "Sales",
                                                       "Office/Administrative Support",
                                                       "Farming/Fishing/Forestry",
                                                       "Construction/Extraction",
                                                       "Installation/Maintenance/Repair",
                                                       "Production",
                                                       "Transportation/Material Moving",
                                                       "Military Specific",
                                                       "Student",
                                                       "Other",
                                                       "More Than One Occupation"))

occupation <- data_final %>%
  group_by(occupation) %>%
  count() %>%
  mutate(percentage = (n/length(data_final$occupation))*100) %>% 
  arrange(desc(n))


occupation$occupation <- factor(occupation$occupation, levels = occupation$occupation[order(occupation$n)])
occupation$occupation  # notice the changed order of factor levels


occupation_plot <- occupation %>%
  ggplot( aes(x=occupation, y=n)) +
  geom_bar(stat="identity", fill="#7570B3FF", alpha=.6, width=.4) +
  coord_flip() +
  xlab("") +
  theme_bw() + theme(axis.ticks = element_line(colour = "black"), 
                     panel.grid.major = element_line(colour = "black", 
                                                     linetype = "blank"), panel.grid.minor = element_line(colour = "black", 
                                                                                                          linetype = "blank"), axis.title = element_text(size = 12), 
                     axis.text = element_text(size = 12, colour = "black"), 
                     axis.text.x = element_text(colour = "black"), 
                     axis.text.y = element_text(colour = "black")) +
  labs(x = NULL, y = "Number of Participants") +
  theme(axis.line = element_line(linetype = "solid"), 
        axis.ticks = element_line(size = 1)) + 
  theme(panel.grid.major = element_line(size = 0.1, 
                                        linetype = "solid")) + 
  labs(title = "Occupation")
occupation_plot
```

##Clean Household
```{r}
data_final$household_makeup <- factor(data_final$household_makeup,
                                              levels = c(1, 2, 3, 4, 5, 6, 7, 8),
                                              labels = c("live alone", 
                                                         "live with roommate or housemate",
                                                         "live with partner",
                                                         "live with partner and children under 18 years old",
                                                         "live with partner and relative over the age of 65 years old",
                                                         "live with children under 18 years old (no partner)",
                                                         "live with relative over the age of 65 years old (no partner)",
                                                         "other"))

household_makeup <- data_final %>%
  group_by(household_makeup) %>%
  count() %>%
  mutate(percentage = (n/length(data_final$household_makeup))*100) %>% 
  arrange(desc(n))


household_makeup$household_makeup <- factor(household_makeup$household_makeup, levels = household_makeup$household_makeup[order(household_makeup$n)])
household_makeup$household_makeup  # notice the changed order of factor levels


household_plot <- household_makeup %>%
  ggplot( aes(x=household_makeup, y=n)) +
  geom_bar(stat="identity", fill="#1B9E77FF", alpha=.6, width=.4) +
  coord_flip() +
  xlab("") +
  theme_bw() + theme(axis.ticks = element_line(colour = "black"), 
                     panel.grid.major = element_line(colour = "black", 
                                                     linetype = "blank"), panel.grid.minor = element_line(colour = "black", 
                                                                                                          linetype = "blank"), axis.title = element_text(size = 12), 
                     axis.text = element_text(size = 12, colour = "black"), 
                     axis.text.x = element_text(colour = "black"), 
                     axis.text.y = element_text(colour = "black")) +
  labs(x = NULL, y = "Number of Participants") +
  theme(axis.line = element_line(linetype = "solid"), 
        axis.ticks = element_line(size = 1)) + 
  theme(panel.grid.major = element_line(size = 0.1, 
                                        linetype = "solid")) + 
  labs(title = "Household Makeup")
household_plot


data_final$household_conflict <- factor(data_final$household_conflict,
                                              levels = c(1, 2, 3, 4, 5),
                                              labels = c("Strongly disagree", 
                                                         "Somewhat disagree",
                                                         "Neither agree nor disagree",
                                                         "Somewhat agree",
                                                         "Strongly agree"))

data_final %>%
  group_by(household_conflict) %>%
  count()
```

##Clean Recruitment Source
```{r}
data_final$recruitment_source <- factor(data_final$recruitment_source,
                                              levels = c(1, 2, 3, 4),
                                              labels = c("Twitter", 
                                                         "Facebook",
                                                         "Instagram",
                                                         "Other"))

data_final$Recruitment_source_self_describe <- as.character(data_final$Recruitment_source_self_describe)

to_reddit <- c("redd","Redd","r/","rebbit","R/","Readit","RED","Redit")

for(i in to_reddit){
  data_final$Recruitment_source_self_describe[grepl(i, data_final$Recruitment_source_self_describe)] <- "Reddit"
}

data_final %>%
  group_by(Recruitment_source_self_describe) %>%
  count() %>%
  arrange(desc(n))

to_wom <- c("Friend","friend","Ben","co-worker","colleague","mom","brother","supervisor","partner","sent","Roommate","shared","Sister","door.com")

for(i in to_wom){
  data_final$Recruitment_source_self_describe[grepl(i, data_final$Recruitment_source_self_describe)] <- "Word of Mouth"
}

to_other <- c("https://docs.google.com/spreadsheets/d/","handbook")

for(i in to_other){
  data_final$Recruitment_source_self_describe[grepl(i, data_final$Recruitment_source_self_describe)] <- "Other"
}

data_final %>%
  group_by(Recruitment_source_self_describe) %>%
  count() %>%
  arrange(desc(n))

data_final$recruitment_source <- as.character(data_final$recruitment_source)

data_final <- data_final %>% 
  mutate(recruitment_source = ifelse(recruitment_source == "Other" & !is.na(Recruitment_source_self_describe), Recruitment_source_self_describe, recruitment_source)) 

data_final <- data_final %>%
  mutate(recruitment_source = replace_na(recruitment_source,"No Response Provided")) 

data_final$recruitment_source <- as.factor(data_final$recruitment_source)

recruitment_source <- data_final %>%
  group_by(recruitment_source) %>%
  count() %>%
  mutate(percentage = (n/length(data_final$recruitment_source))*100) %>% 
  arrange(desc(n))


recruitment_source$recruitment_source <- factor(recruitment_source$recruitment_source, levels = recruitment_source$recruitment_source[order(recruitment_source$n)])
recruitment_source$recruitment_source  # notice the changed order of factor levels


recruitment_plot <- recruitment_source %>%
  ggplot( aes(x=recruitment_source, y=n)) +
  geom_bar(stat="identity", fill="#E6AB02FF", alpha=.6, width=.4) +
  coord_flip() +
  xlab("") +
  theme_bw() + theme(axis.ticks = element_line(colour = "black"), 
                     panel.grid.major = element_line(colour = "black", 
                                                     linetype = "blank"), panel.grid.minor = element_line(colour = "black", 
                                                                                                          linetype = "blank"), axis.title = element_text(size = 12), 
                     axis.text = element_text(size = 12, colour = "black"), 
                     axis.text.x = element_text(colour = "black"), 
                     axis.text.y = element_text(colour = "black")) +
  labs(x = NULL, y = "Number of Participants") +
  theme(axis.line = element_line(linetype = "solid"), 
        axis.ticks = element_line(size = 1)) + 
  theme(panel.grid.major = element_line(size = 0.1, 
                                        linetype = "solid")) + 
  labs(title = "Recruitment Source")
recruitment_plot

```


###Numeric
```{r}
# Change variables to numeric
cols_num <- c("phq_total", 
              "gad_total",
              "zipcode", 
              "flu_sxs_other_number", 
              "hospitalized_number", 
              "passed_away_number", 
              "age",
              "confirmed",
              "deaths",
              "recovered",
              "deaths_country",
              "recovered_country",
              "deaths_world",
              "recovered_world",
              "confirmed_country",
              "confirmed_world"
              )
data_final[, cols_num] %<>%
  lapply(function(x) as.numeric(as.character(x)))
```

##Age
```{r}
describe(data_final$age)

#age <- data_final %>%
 # group_by(age) %>%
 # count()

#age_plot <- age %>%
#  ggplot( aes(x=n, y=age)) +
#  geom_bar(stat="identity", fill="#f68060", alpha=.6, width=.4) +
#  coord_flip() +
#  xlab("") +
#  theme_bw() + theme(axis.ticks = element_line(colour = "black"), 
 #                    panel.grid.major = element_line(colour = "black", 
#                                                     linetype = "blank"), panel.grid.minor = element_line(colour = "black", 
#                                                                                                          linetype = "blank"), axis.title = #element_text(size = 12), 
 #                    axis.text = element_text(size = 12, colour = "black"), 
  #                   axis.text.x = element_text(colour = "black"), 
  #                   axis.text.y = element_text(colour = "black")) +
 # labs(x = "Number of Participants", y = "Age") +
 # theme(axis.line = element_line(linetype = "solid"), 
 #       axis.ticks = element_line(size = 1)) + 
#  theme(panel.grid.major = element_line(size = 0.1, 
#                                        linetype = "solid"))+
#  labs(title = "Age")
#age_plot

```

##Time to complete survey
```{r}
describe((data_final$duration_secs)/60)
```




#Map
```{r}
data_final$lat_n <- as.numeric(data_final$latitude)
data_final$long_n <- as.numeric(data_final$longitude)

#Remove lat and long NAs
#map_data <- dplyr::filter(data_final, data_final$long_n != "NA")
#map_data <- dplyr::filter(data_final, data_final$lat_n != "NA")

map_data <- data_final %>%
  drop_na(lat_n,long_n)

map_data <- map_data %>% 
  dplyr::filter(!(country == "United Kingdom" & city == "Cambridge"))
map_data <- map_data %>% 
  dplyr::filter(!(country == "United States" & city == "New Kensington"))


globe_figure <- leaflet(map_data) %>% 
  addProviderTiles(providers$OpenStreetMap) %>%
  setView( 178, -20, 5 ) %>%
  addHeatmap(lng = ~long_n, lat = ~lat_n,
             blur = 20, max = 0.8, radius = 15) %>% 
  addCircleMarkers(~long_n, ~lat_n, 
                   radius = 1,
                   stroke = FALSE, 
                   fillOpacity = .5,
                   label = ~as.character(city)) %>% 
  addMiniMap(tiles = providers$OpenStreetMap,
             toggleDisplay = TRUE)
globe_figure
```

#Demographic Figures
```{r}
#Identity Plot
identity_plot <- ggpubr::ggarrange(race_plot, ethnicity_plot, gender_plot, political_plot, education_plot, income_plot,
                  labels = c("A", "B", "C", "D", "E", "F"),
                  ncol = 2, nrow = 3)
identity_plot

#Health Plot
health_plot <- ggpubr::ggarrange(covid_concern_plot, covid_test_plot, flu_personal_plot, flu_other_plot, hospitalized_plot, passed_away_plot,
                  labels = c("A", "B", "C", "D", "E", "F"),
                  ncol = 2, nrow = 3)
health_plot

#Finance Plot
finance_plot <- ggpubr::ggarrange(occupation, income_lost_plot, job_lost_plot, money_situation_plot, food_security_plot,
                  labels = c("A", "B", "C", "D", "E"),
                  ncol = 2, nrow = 3)
finance_plot

finance_plot2 <- (income_lost_plot + job_lost_plot) /
(money_situation_plot + food_security_plot)

finance_plot2


#Behavior Plot
behavior_plot <- ggpubr::ggarrange(lifestyle_changes_plot, quarantine_plot,
                  labels = c("A", "B"),
                  ncol = 2, nrow = 1)

behavior_plot

#Recruitment Plot
recruitment_plot <- ggpubr::ggarrange(recruitment_plot,
                  labels = c("A"),
                  ncol = 1, nrow = 1)
recruitment_plot

identity_plot + health_plot
 
occupation_plot
 
finance_plot2 / behavior_plot


#1B9E77FF
#D95F02FF
#7570B3FF
#66A61EFF
#E6AB02FF


```



#Analysis 1: Comparing GAD and PHQ Scores to Historical Data
##Analysis 1a: Comparing GAD and PHQ Mean Scores to Historical Data

###General Population Values and Threshold Values
Löwe, B., Wahl, I., Rose, M., Spitzer, C., Glaesmer, H., Wingenfeld, K., ... & Brähler, E. (2010). A 4-item measure of depression and anxiety: validation and standardization of the Patient Health Questionnaire-4 (PHQ-4) in the general population. Journal of affective disorders, 122(1-2), 86-95.
```{r}
threshold <- 3.0
gad_pop_mean <- 0.82
gad_pop_se <- 1.10
phq_pop_mean <- 0.94
phq_pop_se <- 1.20
```

###Gad Figure
```{r}
gad_descriptives <- describe(data_final$gad_total)
gad_descriptives <- gad_descriptives %>% 
  dplyr::select(mean, sd)
names(gad_descriptives)[names(gad_descriptives) == "mean"] <- "gad_mean"
names(gad_descriptives)[names(gad_descriptives) == "sd"] <- "gad_sd"
gad_descriptives$gad_measure <- "Gad Measure"


#gp_mean <- "General Population Mean: 0.82"
#gad_cuttoff <- "GAD-2 Dx Cuttoff"

Line = c("General Population Average \nGAD-2 Score","GAD-2 Diagnosis \nCutoff Score")
score = as.numeric(c(0.82,3))
lines <- data.frame(Line,score)
lines$Line <- as.factor(lines$Line)
lines$Line <- relevel(lines$Line, "General Population Average \nGAD-2 Score")
gad_figure <- ggplot(gad_descriptives,aes(x=gad_measure, y=gad_mean,fill=gad_mean)) +
  geom_bar(stat="identity", fill="#1B9E77FF",width=0.4) + 
  geom_errorbar(aes(ymin=gad_mean - gad_sd, ymax= gad_mean + gad_sd),width=0.2, linetype = "longdash", color = "black", alpha = 0.4) +
  theme(aspect.ratio = 2/1) +
  geom_text(aes(1.5,2.8,label = "3.0")) +
  geom_text(aes(1.5,.62,label = ".82")) +
  geom_hline(data=lines, aes(yintercept = score, linetype=Line, color = Line)) +
  ylab("GAD-2 Score Range") +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"),axis.text.x=element_blank()) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),axis.line=element_blank()) +
  scale_y_continuous(expand = c(0,0),limits = c(0,6)) +
  theme(axis.line = element_line(linetype = "solid"), 
        axis.ticks = element_line(colour = "black"), 
        axis.title = element_text(size = 12), 
        axis.text = element_text(size = 12, colour = "black"), 
        axis.text.y = element_text(colour = "black"), 
        legend.key = element_rect(fill = "white"), 
        legend.background = element_rect(fill = "white"), 
        legend.position = "bottom") +labs(x = "GAD-2 Measure", fill = NULL)+labs(colour = NULL, linetype = NULL)  +
  scale_colour_manual(values = c("black","red"))

gad_figure
```

###PHQ Figure
```{r}
phq_descriptives <- describe(data_final$phq_total)
phq_descriptives <- phq_descriptives %>% 
  dplyr::select(mean, sd)
names(phq_descriptives)[names(phq_descriptives) == "mean"] <- "phq_mean"
names(phq_descriptives)[names(phq_descriptives) == "sd"] <- "phq_sd"
phq_descriptives$phq_measure <- "phq measure"

#colnames(phq_descriptives) <- c("phq_mean", "phq_sd", "measure")
#phq_descriptives %>% dplyr::add_column(phq_score = 0:6)
#gp_mean <- "General Population Mean: 0.82"
#phq_cuttoff <- "GAD-2 Dx Cuttoff"

Line = c("General Population Average \nPHQ-2 Score","PHQ-2 Diagnosis \nCutoff Score")
score = as.numeric(c(0.94,3.0))
lines <- data.frame(Line,score)
lines$Line <- as.factor(lines$Line)
#lines$Line <- relevel(lines$Line, "PHQ-2 Diagnosis \nCuttoff Score")

phq_figure <- ggplot(phq_descriptives,aes(x=phq_measure, y=phq_mean,fill=phq_mean)) +
  geom_bar(stat="identity", fill="#D95F02FF",width=0.4) + 
  geom_errorbar(aes(ymin=phq_mean - phq_sd, ymax= phq_mean + phq_sd),width=0.2, linetype = "longdash", color = "black", alpha = 0.4) +
  theme(aspect.ratio = 2/1) +
  geom_text(aes(1.5,2.8,label = "3.0")) +
  geom_text(aes(1.5,.74,label = ".94")) +
  geom_hline(data=lines, aes(yintercept = score, linetype=Line, color = Line)) +
  ylab("PHQ-2 Score Range") +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"),axis.text.x=element_blank()) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),axis.line=element_blank()) +
  scale_y_continuous(expand = c(0,0),limits = c(0,6)) +
  theme(axis.line = element_line(linetype = "solid"), 
        axis.ticks = element_line(colour = "black"), 
        axis.title = element_text(size = 12), 
        axis.text = element_text(size = 12, colour = "black"), 
        axis.text.y = element_text(colour = "black"), 
        legend.key = element_rect(fill = "white"), 
        legend.background = element_rect(fill = "white"), 
        legend.position = "bottom") +labs(x = "PHQ-2 Measure", fill = NULL)+labs(colour = NULL, linetype = NULL)  +
  scale_colour_manual(values = c( "black", "red"))

phq_figure
```

```{r}
ggpubr::ggarrange(gad_figure, phq_figure,
          labels = c("A", "B"),
          ncol = 2, nrow = 1)
```

##Analysis 1b: Comparing GAD and PHQ Diagnosis to 12-Month Prevalence Rate
```{r}
#GAD Dx Threshold Percent
gad_dx <- data_final %>% 
  dplyr::select(c(gad_total, covid_concern))

gad_dx <- gad_dx %>% 
  mutate(dx_threshold = ifelse(gad_total %in% '0', "0",
                               ifelse(gad_total %in% '1', "0",
                                      ifelse(gad_total %in% '2', "0", "1"))))

gad_dx$dx_threshold <- factor(gad_dx$dx_threshold,
                                  levels = c(0, 1),
                                  labels = c("Healthy", 
                                             "GAD Dx"))

data.table::setDT(gad_dx)
gad_dx <- gad_dx %>% 
  dplyr::select(-country_region, -province_state)

gad_dx <- gad_dx %>%
    group_by(dx_threshold) %>%
    count() %>%
  mutate(percentage = (n/length(gad_dx$dx_threshold))*100)

#PHQ Dx Threshold Percent
phq_dx <- data_final %>% 
  dplyr::select(c(phq_total, covid_concern))

phq_dx <- phq_dx %>% 
  mutate(dx_threshold = ifelse(phq_total %in% '0', "0",
                               ifelse(phq_total %in% '1', "0",
                                      ifelse(phq_total %in% '2', "0", "1"))))

phq_dx$dx_threshold <- factor(phq_dx$dx_threshold,
                                  levels = c(0, 1),
                                  labels = c("Healthy", 
                                             "PHQ Dx"))

data.table::setDT(phq_dx)
phq_dx <- phq_dx %>% 
  dplyr::select(-country_region, -province_state)

phq_dx <- phq_dx %>%
    group_by(dx_threshold) %>%
    count() %>%
  mutate(percentage = (n/length(phq_dx$dx_threshold))*100)
```

```{r}
#GAD Single-sample T-test

gad_t <- tidy(t.test(data_final$gad_total, mu = .82))

gad_t

```

```{r}
#PHQ Single-sample T-test

phq_t <- tid(t.test(data_final$phq_total, mu = .94))

phq_t
```


#Analyses 2: GAD, PHQ, and Infection by COVID Concern
##Analysis 2a: Gad by COVID Concern
###Figures
```{r}
#Anova Figure
# for reproducibility
set.seed(123)
data.table::setDT(data_final)
gad_anova_figure <- ggstatsplot::ggbetweenstats(
  data = data_final,
  x = covid_concern,
  y = gad_total,
  title = "GAD by Covid Concern",
  messages = FALSE,
  xlab = "COVID-19 Concern",
  ylab = "GAD Score",
  pairwise.comparisons = TRUE, # display significant pairwise comparisons
  pairwise.annotation = "p.value", # how do you want to annotate the pairwise comparisons
  p.adjust.method = "bonferroni") # method for adjusting p-values for multiple comparisons
  # adding new components to `ggstatsplot` default
gad_anova_figure

#Barplot Figure
#GAD Table
gad_table <- data_final %>% 
  dplyr::select(c(gad_total, covid_concern))

gad_table <- gad_table %>% 
  mutate(dx_threshold = ifelse(gad_total %in% '0', "0",
                               ifelse(gad_total %in% '1', "0",
                                      ifelse(gad_total %in% '2', "0", "1"))))

gad_table$dx_threshold <- factor(gad_table$dx_threshold,
                                  levels = c(0, 1),
                                  labels = c("Healthy", 
                                             "GAD Dx"))

data.table::setDT(gad_table)


library(extrafont)

set.seed(123)
gad_plot_figure <- ggstatsplot::ggbarstats(
  data = gad_table,
  x = dx_threshold,
  y = covid_concern,
  size=1,
  sampling.plan = "jointMulti",
  x.axis.orientation = "slant",
  #ggtheme = hrbrthemes::theme_modern_rc(),
  ggstatsplot.layer = FALSE,
  ggplot.component = ggplot2::theme(axis.text.x = ggplot2::element_text(face = "italic"),text = element_text(size = 20),legend.title = element_blank()),
  palette = "Set2",
  messages = FALSE
)


gad_plot_figure

#Gad Pie Chart
gad_pie <- ggstatsplot::ggpiestats(
  data = gad_table,
  x = dx_threshold,
  y = covid_concern,
  title = "GAD Dx by COVID-19 Concern", # title for the plot
  legend.title = "Diagnostic Threshold", # title for the legend
  factor.levels = c("1 = GAD Dx", "0 = No Dx"), # renaming the factor level names (`x`)
  messages = FALSE)
gad_pie

#Combine Figures
ggpubr::ggarrange(gad_anova_figure, gad_plot_figure,
                  labels = c("A", "B"),
                  ncol = 1, nrow = 2)
```

###MLM GAD by COVID Concern
```{r}

data_final$covid_concern_integer <- as.integer(data_final$covid_concern)

#Unadjusted Model
# Check for homogeneity of variance
#leveneTest(covid_concern_integer ~ gad_total, center = mean, data = data_final)

# ANCOVA
gad_covid_model_unadjusted <- lmer(covid_concern_integer ~ gad_total + (1|country_region), data = drop_na(data_final,age,gender_cleaned),REML=FALSE)
summary(gad_covid_model_unadjusted)
sjPlot::tab_model(gad_covid_model_unadjusted)
#effectsize::cohens_f(gad_covid_model_unadjusted)
sjstats::anova_stats(gad_covid_model_unadjusted)
AIC(gad_covid_model_unadjusted)
BIC(gad_covid_model_unadjusted)


# Check residuals for normality
gad_covid_model_residuals_unadjusted <- resid(gad_covid_model_unadjusted)
shapiro.test(gad_covid_model_residuals_unadjusted)

#Adjusted Model
# Check for homogeneity of variance
#leveneTest(covid_concern_integer ~ gad_total, center = mean, data = data_final)

# ANCOVA
gad_covid_model_adjusted <- lmer(covid_concern_integer ~ gad_total + age + gender_cleaned + date +  (1|country_region), data = drop_na(data_final,age,gender_cleaned),REML=FALSE)
summary(gad_covid_model_adjusted)
sjPlot::tab_model(gad_covid_model_adjusted)
#effectsize::cohens_f(gad_covid_model_adjusted)
sjstats::anova_stats(gad_covid_model_adjusted)
AIC(gad_covid_model_adjusted)
BIC(gad_covid_model_adjusted)

# Check residuals for normality
gad_covid_model_residuals_adjusted <- resid(gad_covid_model_adjusted)
shapiro.test(gad_covid_model_residuals_adjusted)

#Compare Models
anova(gad_covid_model_unadjusted, gad_covid_model_adjusted)



#Print Table
sjPlot::tab_model(gad_covid_model_unadjusted, gad_covid_model_adjusted,
          pred.labels = c("Intercept", "GAD Score", "Age", "Gender: Woman",  "Gender: Nonbinary","Gender: Prefer to Self Describe","Gender: Prefer not to Answer","Date"),
          dv.labels = c("Unadjusted Model: COVID-19 Concern", "Adjusted Model: COVID-19 Concern"),
          string.ci = "Conf. Int (95%)",
          string.p = "P-Value",
          digits = 3,
          show.icc=FALSE,show.r2=FALSE,show.se=TRUE,
          show.se = TRUE,
          show.aic = TRUE,
          file = "~/Dropbox/COVID-19 Study/Tables/gad_covid_table.doc")
```

##Analyses 2b:PHQ by COVID Concern
###Figures
```{r}

# for reproducibility
set.seed(123)

phq_anova_figure <- ggstatsplot::ggbetweenstats(
  data = data_final,
  x = covid_concern,
  y = phq_total,
  title = "PHQ by Covid Concern",
  xlab = "COVID-19 Concern",
  ylab = "PHQ Score",
  messages = FALSE,
  pairwise.comparisons = TRUE, # display significant pairwise comparisons
  pairwise.annotation = "p.value", # how do you want to annotate the pairwise comparisons
  p.adjust.method = "bonferroni") # method for adjusting p-values for multiple comparisons
  # adding new components to `ggstatsplot` default
phq_anova_figure

#PHQ Table
phq_table <- data_final %>% 
  dplyr::select(c(phq_total, covid_concern))

phq_table <- phq_table %>% 
  mutate(dx_threshold = ifelse(phq_total %in% '0', "0",
                               ifelse(phq_total %in% '1', "0",
                                      ifelse(phq_total %in% '2', "0", "1"))))

phq_table$dx_threshold <- factor(phq_table$dx_threshold,
                                 levels = c(0, 1),
                                 labels = c("Healthy", 
                                            "PHQ Dx"))

data.table::setDT(phq_table)


set.seed(123)


phq_plot_figure <- ggstatsplot::ggbarstats(
  data = phq_table,
  x = dx_threshold,
  y = covid_concern,
  sampling.plan = "jointMulti",
  x.axis.orientation = "slant",
  xlab = "COVID-19 Concern",
  #ggtheme = hrbrthemes::theme_modern_rc(),
  ggstatsplot.layer = FALSE,
  ggplot.component = ggplot2::theme(axis.text.x = ggplot2::element_text(face = "italic"),text = element_text(size = 20),legend.title = element_blank()),
  palette = "Set2",
  messages = FALSE
)

phq_plot_figure

phq_pie <- ggstatsplot::ggpiestats(
  data = phq_table,
  x = dx_threshold,
  y = covid_concern,
  title = "Depression Dx by COVID-19 Concern", # title for the plot
  legend.title = "Diagnostic Threshold", # title for the legend
  factor.levels = c("1 = Depression Dx", "0 = No Dx"), # renaming the factor level names (`x`)
  messages = FALSE)
phq_pie
library(ggpubr)
#Combine Figures
ggpubr::ggarrange(gad_plot_figure, phq_plot_figure,
                  labels = c("A", "B"),
                  ncol = 1, nrow = 2) %>%
  ggexport(filename = "figure.png",width=900,height=1200)
```

##Combine Figures
```{r}
#Combine Figures
# test <- ggpubr::ggarrange(gad_anova_figure, phq_anova_figure,gad_plot_figure, phq_plot_figure,
#                   labels = c("A", "B", "C", "D"),
#                   ncol = 2, nrow = 2) 
# 
# test %>%
#   ggpubr::ggexport(filename = "test.png", width=1000,height=607)
```



###Anova PHQ and Covid Concern
```{r}
# Check for homogeneity of variance
#leveneTest(covid_concern_integer ~ phq_total, center = mean, data = data_final)

# ANCOVA
phq_covid_model_unadjusted <- lmer(covid_concern_integer ~ phq_total + (1|country_region), data = drop_na(data_final,age,gender_cleaned),REML=FALSE)
summary(phq_covid_model_unadjusted)
tab_model(phq_covid_model_unadjusted)
#effectsize::cohens_f(phq_covid_model_unadjusted)
sjstats::anova_stats(phq_covid_model_unadjusted)
AIC(phq_covid_model_unadjusted)
BIC(phq_covid_model_unadjusted)


# Check residuals for normality
phq_covid_model_residuals_unadjusted <- resid(phq_covid_model_unadjusted)
shapiro.test(phq_covid_model_residuals_unadjusted)


#Adjusted Model
# Check for homogeneity of variance
#leveneTest(covid_concern_integer ~ phq_total, center = mean, data = data_final)

# ANCOVA
phq_covid_model_adjusted <- lmer(covid_concern_integer ~ phq_total + age + gender_cleaned + date + (1|country_region), data = drop_na(data_final,age,gender_cleaned),REML=FALSE)
summary(phq_covid_model_adjusted)
tab_model(phq_covid_model_adjusted)
#effectsize::cohens_f(phq_covid_model_adjusted)
sjstats::anova_stats(phq_covid_model_adjusted)
AIC(phq_covid_model_adjusted)
BIC(phq_covid_model_adjusted)

# Check residuals for normality
phq_covid_model_residuals_adjusted <- resid(phq_covid_model_adjusted)
shapiro.test(phq_covid_model_residuals_adjusted)

#Compare Models
anova(phq_covid_model_unadjusted, phq_covid_model_adjusted)

#Print Table
tab_model(phq_covid_model_unadjusted, phq_covid_model_adjusted,
          pred.labels = c("Intercept", "'PHQ Score", "Age", "Gender: Woman",  "Gender: Nonbinary","Gender: Prefer to Self Describe","Gender: Prefer not to Answer","Date"),
          dv.labels = c("Unadjusted Model: COVID-19 Concern", "Adjusted Model: COVID-19 Concern"),
          string.ci = "Conf. Int (95%)",
          string.p = "P-Value",show.icc=FALSE,show.r2=FALSE,show.se=TRUE,
          digits = 3,
          show.se = TRUE,
          show.aic = TRUE,
          file = "~/Dropbox/COVID-19 Study/Tables/phq_covid_table.doc")
```


##World Cases by COVID Concern
```{r}
# for reproducibility
set.seed(123)

world_cases_anova_figure <- ggstatsplot::ggbetweenstats(
  data = data_final,
  x = covid_concern,
  y = confirmed_world,
  title = "World Cases by Covid Concern",
  xlab = "COVID-19 Concern",
  ylab = "Reported World Cases",
  messages = FALSE,
  pairwise.comparisons = TRUE, # display significant pairwise comparisons
  pairwise.annotation = "p.value", # how do you want to annotate the pairwise comparisons
  p.adjust.method = "bonferroni") # method for adjusting p-values for multiple comparisons
# adding new components to `ggstatsplot` default
world_cases_anova_figure

# Log transformed
world_cases_anova_figure_log <- ggstatsplot::ggbetweenstats(
  data = data_final,
  x = covid_concern,
  y = confirmed_world_log,
  title = "World Cases by Covid Concern",
  xlab = "COVID-19 Concern",
  ylab = "Reported World Cases (Log Transformed)",
  messages = FALSE,
  pairwise.comparisons = TRUE, # display significant pairwise comparisons
  pairwise.annotation = "p.value", # how do you want to annotate the pairwise comparisons
  p.adjust.method = "bonferroni") # method for adjusting p-values for multiple comparisons
# adding new components to `ggstatsplot` default
world_cases_anova_figure_log

# Check for homogeneity of variance
leveneTest(confirmed_world ~ covid_concern, center = mean, data = data_final)

# ANCOVA
world_cases_covid_model_unadjusted <- lmer(covid_concern_integer ~ confirmed_world_log  + (1|country_region), data = drop_na(data_final,age,gender_cleaned),REML=FALSE) # I changed the dependent variable to the log transformed variable
summary(world_cases_covid_model_unadjusted)
tab_model(world_cases_covid_model_unadjusted)
#effectsize::cohens_f(world_cases_covid_model_unadjusted)
sjstats::anova_stats(world_cases_covid_model_unadjusted)
AIC(world_cases_covid_model_unadjusted)
BIC(world_cases_covid_model_unadjusted)


# Check residuals for normality
world_cases_covid_model_residuals_unadjusted <- resid(world_cases_covid_model_unadjusted)
shapiro.test(world_cases_covid_model_residuals_unadjusted)


#Adjusted Model
# Check for homogeneity of variance
leveneTest(confirmed_world_log ~ covid_concern, center = mean, data = data_final)

# ANCOVA
world_cases_covid_model_adjusted <- lmer(covid_concern_integer ~ confirmed_world_log + age + gender_cleaned + date  +  (1|country_region), data = drop_na(data_final,age,gender_cleaned),REML=FALSE)
summary(world_cases_covid_model_adjusted)
tab_model(world_cases_covid_model_adjusted)
#effectsize::cohens_f(world_cases_covid_model_adjusted)
sjstats::anova_stats(world_cases_covid_model_adjusted)
AIC(world_cases_covid_model_adjusted)
BIC(world_cases_covid_model_adjusted)

# Check residuals for normality
world_cases_covid_model_residuals_adjusted <- resid(world_cases_covid_model_adjusted)
shapiro.test(world_cases_covid_model_residuals_adjusted)

#Compare Models
anova(world_cases_covid_model_unadjusted, world_cases_covid_model_adjusted)

#Print Table
tab_model(world_cases_covid_model_unadjusted, world_cases_covid_model_adjusted,
          pred.labels = c("Intercept", "Confirmed World Cases", "Age", "Gender: Woman",  "Gender: Nonbinary","Gender: Prefer to Self Describe","Gender: Prefer not to Answer","Date"),
          dv.labels = c("Unadjusted Model: COVID-19 Concern", "Adjusted Model: COVID-19 Concern"),
          string.ci = "Conf. Int (95%)",
          string.p = "P-Value",show.icc=FALSE,show.r2=FALSE,show.se=TRUE,
          digits = 3,
          show.se = TRUE,
          show.aic = TRUE,
          file = "~/Dropbox/COVID-19 Study/Tables/world_cases_covid_table.doc")
```

##Country Cases by COVID Concern
```{r}
# for reproducibility
set.seed(123)

#Raw Cases
country_cases_anova_figure <- ggstatsplot::ggbetweenstats(
  data = data_final,
  x = covid_concern,
  y = confirmed_country,
  title = "Country Cases by Covid Concern",
  xlab = "COVID-19 Concern",
  ylab = "Reported Cases in Country",
  messages = FALSE,
  pairwise.comparisons = TRUE, # display significant pairwise comparisons
  pairwise.annotation = "p.value", # how do you want to annotate the pairwise comparisons
  p.adjust.method = "bonferroni") # method for adjusting p-values for multiple comparisons
# adding new components to `ggstatsplot` default
country_cases_anova_figure

#Log transformed
country_cases_anova_figure_log <- ggstatsplot::ggbetweenstats(
  data = data_final,
  x = covid_concern,
  y = confirmed_country_log,
  title = "Country Cases by Covid Concern",
  xlab = "COVID-19 Concern",
  ylab = "Reported Cases in Country (Log Transformed)",
  messages = FALSE,
  pairwise.comparisons = TRUE, # display significant pairwise comparisons
  pairwise.annotation = "p.value", # how do you want to annotate the pairwise comparisons
  p.adjust.method = "bonferroni") # method for adjusting p-values for multiple comparisons
# adding new components to `ggstatsplot` default
country_cases_anova_figure_log

# Check for homogeneity of variance
leveneTest(confirmed_country ~ covid_concern, center = mean, data = data_final)

# ANCOVA
country_cases_covid_model_unadjusted <- lmer(covid_concern_integer ~ confirmed_country_log + (1|country_region), data = drop_na(data_final,age,gender_cleaned),REML=FALSE)
summary(country_cases_covid_model_unadjusted)
tab_model(country_cases_covid_model_unadjusted)
#effectsize::cohens_f(country_cases_covid_model)
sjstats::anova_stats(country_cases_covid_model_unadjusted)
AIC(country_cases_covid_model_unadjusted)
BIC(country_cases_covid_model_unadjusted)


# Check residuals for normality
country_cases_covid_model_residuals_unadjusted <- resid(country_cases_covid_model_unadjusted)
shapiro.test(country_cases_covid_model_residuals_unadjusted)


#Adjusted Model
# Check for homogeneity of variance
#leveneTest(confirmed_country_log ~ covid_concern, center = mean, data = data_final)

# ANCOVA
country_cases_covid_model_adjusted <- lmer(covid_concern_integer ~ confirmed_country_log + age  + gender_cleaned + date + (1|country_region), data = drop_na(data_final,age,gender_cleaned), REML=FALSE)
summary(country_cases_covid_model_adjusted)
tab_model(country_cases_covid_model_adjusted)
#effectsize::cohens_f(world_cases_covid_model_adjusted)
sjstats::anova_stats(country_cases_covid_model_adjusted)
AIC(country_cases_covid_model_adjusted)
BIC(country_cases_covid_model_adjusted)

# Check residuals for normality
country_cases_covid_model_residuals_adjusted <- resid(country_cases_covid_model_adjusted)
shapiro.test(country_cases_covid_model_residuals_adjusted)

#Compare Models
anova(country_cases_covid_model_unadjusted, country_cases_covid_model_adjusted)

#Print Table
tab_model(country_cases_covid_model_unadjusted, country_cases_covid_model_adjusted,
          pred.labels = c("Intercept", "Confirmed Cases Within Country", "Age", "Gender: Woman",  "Gender: Nonbinary","Gender: Prefer to Self Describe","Gender: Prefer not to Answer","Date"),
          dv.labels = c("Unadjusted Model: COVID-19 Concern", "Adjusted Model: COVID-19 Concern"),
          string.ci = "Conf. Int (95%)",
          string.p = "P-Value",show.icc=FALSE,show.r2=FALSE,show.se=TRUE,
          digits = 3,
          show.se = TRUE,
          show.aic = TRUE,
          file = "~/Dropbox/COVID-19 Study/Tables/country_cases_covid_table.doc")
```

##Compare epi to mental health models
```{r}

data_final <- data_final %>% 
  mutate(confirmed_country_log = ifelse(is.na(confirmed_country_log), 0, confirmed_country_log)) 
model_data  <- data_final %>%
  drop_na(covid_concern_integer,gad_total,phq_total,confirmed_country_log,country_region,country_diff_days,days_since_lockdown)

mental_health_model <- lmer(covid_concern_integer ~ gad_total + phq_total+ age + gender_cleaned + date + (1|country_region) , model_data,REML=FALSE)

epi_model <- lmer(covid_concern_integer ~ confirmed_country_log + confirmed_world_log + age +gender_cleaned + date + (1|country_region), model_data,REML=FALSE)

anova(epi_model,mental_health_model)

tab_model(mental_health_model, epi_model,
          pred.labels = c("Intercept", "GAD Score","PHQ Score", "Age", "Gender: Woman",  "Gender: Nonbinary","Gender: Prefer to Self Describe","Gender: Prefer not to Answer","Date","Confirmed Country Cases","Confirmed World Cases"),
          dv.labels = c("Mental Health Model", "Epdemiological Model"),
          string.ci = "Conf. Int (95%)",
          string.p = "P-Value",show.icc=FALSE,show.r2=FALSE,show.se=TRUE,
          digits = 3,
          show.se = TRUE,
          show.aic = TRUE,
          file = "~/Dropbox/COVID-19 Study/Tables/epi_vs_psych_concern_table.doc")

mental_health_model <- lmer(covid_concern_integer ~ gad_total + phq_total + (1|country_region) , model_data,REML=FALSE)

ggstatsplot::ggcoefstats(
  x = mental_health_model,
  xlab = "Regression Coefficient",
  ylab = "Predictor"
)
```

```{r}

full_model_covid_concern <- lmer(covid_concern_integer ~ gad_total + phq_total + confirmed_world_log + confirmed_country_log + age + gender_cleaned + date + (1|country_region) , model_data,REML=FALSE)


tab_model(intermediate_model, pred.labels = c("Intercept", "GAD Score","PHQ Score","Confirmed World Cases", "Confirmed Country Cases", "Age", "Gender: Woman",  "Gender: Nonbinary","Gender: Prefer to Self Describe","Gender: Prefer not to Answer","Date"),
          dv.labels = c("COVID-19 Concern"),
          string.ci = "Conf. Int (95%)",
          string.p = "P-Value",show.icc=FALSE,show.r2=FALSE,show.se=TRUE,
          digits = 3,
          show.aic = TRUE,
          file = "~/Dropbox/COVID-19 Study/Tables/complete_covid_concern_table.doc")


```



#Analysis 3: Behavior Change

##Covid Concern and Behavior Change
```{r}
data_final$covid_concern_num <- as.numeric(data_final$covid_concern)

data_final$self_quarantine_integer <- as.integer(data_final$self_quarantine)

# for reproducibility
#set.seed(123)
#data_final$self_quarantine
#data.table::setDT(data_final)
quarantine_concern_anova_figure <- ggstatsplot::ggbetweenstats(
  data = data_final,
  x = self_quarantine,
  y = covid_concern_num,
  title = "COVID Concern by Behavior Change",
  xlab = "Self Quarantine",
  ylab = "COVID-19 Concern",
  messages = FALSE,
  pairwise.comparisons = TRUE, # display significant pairwise comparisons
  pairwise.annotation = "p.value", # how do you want to annotate the pairwise comparisons
  p.adjust.method = "bonferroni") # method for adjusting p-values for multiple comparisons
# adding new components to `ggstatsplot` default
quarantine_concern_anova_figure

# Check for homogeneity of variance
leveneTest(covid_concern_num ~ self_quarantine, center = mean, data = data_final)

# ANOVA
quarantine_concern_covid_model_unadjusted <- lmer(self_quarantine_integer ~ covid_concern_integer + (1|country_region), data = drop_na(data_final,age,gender_cleaned),REML=FALSE)
summary(quarantine_concern_covid_model_unadjusted)
tab_model(quarantine_concern_covid_model_unadjusted)
#effectsize::cohens_f(quarantine_concern_covid_model_unadjusted)
sjstats::anova_stats(quarantine_concern_covid_model_unadjusted)
AIC(quarantine_concern_covid_model_unadjusted)
BIC(quarantine_concern_covid_model_unadjusted)


# Check residuals for normality
quarantine_concern_covid_model_residuals_unadjusted <- resid(quarantine_concern_covid_model_unadjusted)
shapiro.test(quarantine_concern_covid_model_residuals_unadjusted)


# Check for homogeneity of variance
leveneTest(covid_concern_num ~ self_quarantine, center = mean, data = data_final)

# ANCOVA
quarantine_concern_covid_model_adjusted <- lmer(self_quarantine_integer ~ covid_concern_integer + gender_cleaned + age + date + (1|country_region), data = drop_na(data_final,age,gender_cleaned),REML=FALSE)
summary(quarantine_concern_covid_model_adjusted)
tab_model(quarantine_concern_covid_model_adjusted)
#effectsize::cohens_f(quarantine_concern_covid_model_unadjusted)
sjstats::anova_stats(quarantine_concern_covid_model_adjusted)
AIC(quarantine_concern_covid_model_adjusted)
BIC(quarantine_concern_covid_model_adjusted)

levels(data_final$self_quarantine)

# Check residuals for normality
quarantine_concern_covid_model_residuals_adjusted <- resid(quarantine_concern_covid_model_adjusted)
shapiro.test(quarantine_concern_covid_model_residuals_adjusted)

anova(quarantine_concern_covid_model_unadjusted,quarantine_concern_covid_model_adjusted)

tab_model(quarantine_concern_covid_model_unadjusted, quarantine_concern_covid_model_adjusted,
          pred.labels = c("Intercept", "COVID-19 Concern", "Age", "Gender: Woman",  "Gender: Nonbinary","Gender: Prefer to Self Describe","Gender: Prefer not to Answer","Date"),
          dv.labels = c("Unadjusted Model: Self Quarantine", "Adjusted Model: Self Quarantine"),
          string.ci = "Conf. Int (95%)",
          string.p = "P-Value",show.icc=FALSE,show.r2=FALSE,show.se=TRUE,
          digits = 3,
          show.aic = TRUE,
          file = "~/Dropbox/COVID-19 Study/Tables/quarantine_covid_table.doc")
```


```{r}
mental_model_q <- lmer(self_quarantine_integer ~ phq_total  + gad_total + gender_cleaned + age + date + (1|country_region), data = drop_na(data_final,age,gender_cleaned,covid_concern_num,phq_total,gad_total),REML=FALSE)

epi_model_q <- lmer(self_quarantine_integer ~ confirmed_country_log  + confirmed_world_log + gender_cleaned + age + date + (1|country_region), data = drop_na(data_final,age,gender_cleaned,covid_concern_num,phq_total,gad_total),REML=FALSE)               
                         
                         
covid_model_q <- lmer(self_quarantine_integer ~ covid_concern_num + gender_cleaned + age + date + (1|country_region), data = drop_na(data_final,age,gender_cleaned,covid_concern_num,phq_total,gad_total),REML=FALSE)

tab_model(epi_model_q,
          pred.labels = c("Intercept", "Confirmed Country Cases", "Confirmed World Cases", "Gender: Woman",  "Gender: Nonbinary","Gender: Prefer to Self Describe","Gender: Prefer not to Answer","Age","Date"),
          dv.labels = c("Self Quarantine"),
          string.ci = "Conf. Int (95%)",
          string.p = "P-Value",show.icc=FALSE,show.r2=FALSE,show.se=TRUE,
          digits = 3,
          show.aic = TRUE,
          file = "~/Dropbox/COVID-19 Study/Tables/quarantine_epi_table.doc")
``` 


```{r}
full_model_q <- lmer(self_quarantine_integer ~ phq_total  + gad_total + confirmed_country_log  + confirmed_world_log + covid_concern_integer + gender_cleaned + age + date + (1|country_region), data = drop_na(data_final,age,gender_cleaned,covid_concern_integer,phq_total,gad_total),REML=FALSE)

tab_model(full_model_q,pred.labels = c("Intercept", "PHQ Score","GAD Score","Confirmed Country Cases", "Confirmed World Cases", "COVID-19 Concern", "Age", "Gender: Woman",  "Gender: Nonbinary","Gender: Prefer to Self Describe","Gender: Prefer not to Answer","Date"),
          dv.labels = c("Mental Health Model"),
          string.ci = "Conf. Int (95%)",
          string.p = "P-Value",show.icc=FALSE,show.r2=FALSE,show.se=TRUE,
          digits = 3,
          show.aic = TRUE,
          file = "~/Dropbox/COVID-19 Study/Tables/complete_quarantine_table.doc")


```


##GAD and Behavior Change
```{r}
# for reproducibility
set.seed(123)


quarantine_gad_anova_figure <- ggstatsplot::ggbetweenstats(
  data = data_final,
  x = self_quarantine,
  y = gad_total,
  title = "GAD by Behavior Change",
  xlab = "Self Quarantine",
  ylab = "GAD Score",
  messages = FALSE,
  pairwise.comparisons = TRUE, # display significant pairwise comparisons
  pairwise.annotation = "p.value", # how do you want to annotate the pairwise comparisons
  p.adjust.method = "bonferroni") # method for adjusting p-values for multiple comparisons
# adding new components to `ggstatsplot` default
quarantine_gad_anova_figure

# Check for homogeneity of variance
#leveneTest(gad_total ~ self_quarantine, center = mean, data = data_final)

# ANOVA
quarantine_gad_model_unadjusted <- lmer(self_quarantine_integer ~ gad_total + (1|country_region) , data = drop_na(data_final,age,gender_cleaned),REML=FALSE)
summary(quarantine_gad_model_unadjusted)
tab_model(quarantine_gad_model_unadjusted)
#effectsize::cohens_f(quarantine_gad_model)
sjstats::anova_stats(quarantine_gad_model_unadjusted)
AIC(quarantine_gad_model_unadjusted)
BIC(quarantine_gad_model_unadjusted)


# Check residuals for normality
quarantine_gad_model_residuals_unadjusted <- resid(quarantine_gad_model_unadjusted)
shapiro.test(quarantine_gad_model_residuals_unadjusted)

# ANOVA
quarantine_gad_model_adjusted <- lmer(self_quarantine_integer ~ gad_total + age + gender_cleaned + date + (1|country_region) , data = drop_na(data_final,age,gender_cleaned,gad_total,phq_total),REML=FALSE)
summary(quarantine_gad_model_adjusted)
tab_model(quarantine_gad_model_adjusted)
#effectsize::cohens_f(quarantine_gad_model)
sjstats::anova_stats(quarantine_gad_model_adjusted)
AIC(quarantine_gad_model_adjusted)
BIC(quarantine_gad_model_adjusted)


# Check residuals for normality
quarantine_gad_model_residuals_adjusted <- resid(quarantine_gad_model_adjusted)
shapiro.test(quarantine_gad_model_residuals_adjusted)

anova(quarantine_gad_model_unadjusted,quarantine_gad_model_adjusted)

tab_model(quarantine_gad_model_unadjusted, quarantine_gad_model_adjusted,
          pred.labels = c("Intercept", "GAD Score", "Age", "Gender: Woman",  "Gender: Nonbinary","Gender: Prefer to Self Describe","Gender: Prefer not to Answer","Date"),
          dv.labels = c("Unadjusted Model: Self Quarantine", "Adjusted Model: Self Quarantine"),
          string.ci = "Conf. Int (95%)",
          string.p = "P-Value",show.icc=FALSE,show.r2=FALSE,show.se=TRUE,
          digits = 3,
          show.aic = TRUE,
          file = "~/Dropbox/COVID-19 Study/Tables/quarantine_gad_table.doc")
```

##PHQ and Behavior Change
```{r}
# for reproducibility
set.seed(123)

quarantine_phq_anova_figure <- ggstatsplot::ggbetweenstats(
  data = data_final,
  x = self_quarantine,
  y = phq_total,
  title = "PHQ by Behavior Change",
  xlab = "Self Quarantine",
  ylab = "PHQ Score",
  messages = FALSE,
  pairwise.comparisons = TRUE, # display significant pairwise comparisons
  pairwise.annotation = "p.value", # how do you want to annotate the pairwise comparisons
  p.adjust.method = "bonferroni") # method for adjusting p-values for multiple comparisons
# adding new components to `ggstatsplot` default
quarantine_phq_anova_figure

# Check for homogeneity of variance
leveneTest(phq_total ~ self_quarantine, center = mean, data = data_final)

# ANCOVA
quarantine_phq_model_unadjusted <- lmer(self_quarantine_integer ~ phq_total +  (1|country), data = drop_na(data_final,age,gender_cleaned),REML=FALSE)
summary(quarantine_phq_model_unadjusted)
tab_model(quarantine_phq_model_unadjusted)
#effectsize::cohens_f(quarantine_phq_model)
sjstats::anova_stats(quarantine_phq_model_unadjusted)
AIC(quarantine_phq_model_unadjusted)
BIC(quarantine_phq_model_unadjusted)


# Check residuals for normality
quarantine_phq_model_residuals_unadjusted <- resid(quarantine_phq_model_unadjusted)
shapiro.test(quarantine_phq_model_residuals_unadjusted)


# Adjusted
quarantine_phq_model_adjusted <- lmer(self_quarantine_integer ~ phq_total + age + gender_cleaned + date + (1|country), data = drop_na(data_final,age,gender_cleaned,gad_total,phq_total),REML=FALSE)
summary(quarantine_phq_model_adjusted)
tab_model(quarantine_phq_model_adjusted)
#effectsize::cohens_f(quarantine_phq_model)
sjstats::anova_stats(quarantine_phq_model_adjusted)
AIC(quarantine_phq_model_adjusted)
BIC(quarantine_phq_model_adjusted)


# Check residuals for normality
quarantine_phq_model_residuals_adjusted <- resid(quarantine_phq_model_adjusted)
shapiro.test(quarantine_phq_model_residuals_adjusted)

anova(quarantine_phq_model_unadjusted,quarantine_phq_model_adjusted)

tab_model(quarantine_phq_model_unadjusted, quarantine_phq_model_adjusted,
          pred.labels = c("Intercept", "PHQ Score", "Age", "Gender: Woman",  "Gender: Nonbinary","Gender: Prefer to Self Describe","Gender: Prefer not to Answer","Date"),
          dv.labels = c("Unadjusted Model: Self Quarantine", "Adjusted Model: Self Quarantine"),
          string.ci = "Conf. Int (95%)",
          string.p = "P-Value",show.icc=FALSE,show.r2=FALSE,show.se=TRUE,
          digits = 3,
          show.aic = TRUE,
          file = "~/Dropbox/COVID-19 Study/Tables/quarantine_PHQ_table.doc")
```

```{r}
# Adjusted
quarantine_mental_model_adjusted <- lmer(self_quarantine_integer ~ phq_total + gad_total + age + gender_cleaned + date + (1|country), data = drop_na(data_final,age,gender_cleaned,gad_total,phq_total),REML=FALSE)

tab_model(quarantine_mental_model_adjusted,
          pred.labels = c("Intercept", "PHQ Score", "GAD Score","Age", "Gender: Woman",  "Gender: Nonbinary","Gender: Prefer to Self Describe","Gender: Prefer not to Answer","Date"),
          dv.labels = c("Self Quarantine"),
          string.ci = "Conf. Int (95%)",
          string.p = "P-Value",show.icc=FALSE,show.r2=FALSE,show.se=TRUE,
          digits = 3,
          show.aic = TRUE,
          file = "~/Dropbox/COVID-19 Study/Tables/quarantine_mental_table.doc")
```


##Total World Cases and Behavior Change
```{r}
# for reproducibility
set.seed(123)

#raw cases
quarantine_world_total_anova_figure <- ggstatsplot::ggbetweenstats(
  data = data_final,
  x = self_quarantine,
  y = confirmed_world,
  title = "Total World Cases by Behavior Change",
  xlab = "Self Quarantine",
  ylab = "Reported World Cases",
  messages = FALSE,
  pairwise.comparisons = TRUE, # display significant pairwise comparisons
  pairwise.annotation = "p.value", # how do you want to annotate the pairwise comparisons
  p.adjust.method = "bonferroni") # method for adjusting p-values for multiple comparisons
# adding new components to `ggstatsplot` default
quarantine_world_total_anova_figure

#log transformed cases
quarantine_world_total_anova_figure_log <- ggstatsplot::ggbetweenstats(
  data = data_final,
  x = self_quarantine,
  y = confirmed_world_log,
  title = "Total World Cases by Behavior Change",
  xlab = "Self Quarantine",
  ylab = "Reported World Cases (Log Transformed)",
  messages = FALSE,
  pairwise.comparisons = TRUE, # display significant pairwise comparisons
  pairwise.annotation = "p.value", # how do you want to annotate the pairwise comparisons
  p.adjust.method = "bonferroni") # method for adjusting p-values for multiple comparisons
# adding new components to `ggstatsplot` default
quarantine_world_total_anova_figure_log

# Check for homogeneity of variance
leveneTest(confirmed_world ~ self_quarantine, center = mean, data = data_final)

# ANCOVA
quarantine_world_total_model_unadjusted <- lmer(self_quarantine_integer ~ confirmed_world_log + (1|country_region) , data = drop_na(data_final,age,gender_cleaned),REML=FALSE)
summary(quarantine_world_total_model_unadjusted)
tab_model(quarantine_world_total_model_unadjusted)
#effectsize::cohens_f(quarantine_world_total_model)
sjstats::anova_stats(quarantine_world_total_model_unadjusted)
AIC(quarantine_world_total_model_unadjusted)
BIC(quarantine_world_total_model_unadjusted)


# Check residuals for normality
quarantine_world_total_model_residuals_unadjusted <- resid(quarantine_world_total_model_unadjusted)
shapiro.test(quarantine_world_total_model_residuals_unadjusted)

# Adjusted
quarantine_world_total_model_adjusted <- lmer(self_quarantine_integer ~ confirmed_world_log + age + gender_cleaned + date + (1|country_region) , data = drop_na(data_final,age,gender_cleaned),REML=FALSE)
summary(quarantine_world_total_model_adjusted)
tab_model(quarantine_world_total_model_adjusted)
#effectsize::cohens_f(quarantine_world_total_model)
sjstats::anova_stats(quarantine_world_total_model_adjusted)
AIC(quarantine_world_total_model_adjusted)
BIC(quarantine_world_total_model_adjusted)


# Check residuals for normality
quarantine_world_total_model_residuals_adjusted <- resid(quarantine_world_total_model_adjusted)
shapiro.test(quarantine_world_total_model_residuals_adjusted)

anova(quarantine_world_total_model_unadjusted,quarantine_world_total_model_adjusted)

tab_model(quarantine_world_total_model_unadjusted, quarantine_world_total_model_adjusted,
          pred.labels = c("Intercept", "Confirmed World Cases", "Age", "Gender: Woman",  "Gender: Nonbinary","Gender: Prefer to Self Describe","Gender: Prefer not to Answer","Date"),
          dv.labels = c("Unadjusted Model: Self Quarantite", "Adjusted Model: Self Quarantine"),
          string.ci = "Conf. Int (95%)",
          string.p = "P-Value",show.icc=FALSE,show.r2=FALSE,show.se=TRUE,
          digits = 3,
          show.aic = TRUE,
          file = "~/Dropbox/COVID-19 Study/Tables/quarantine_TWC_table.doc")
```

##Total Country Cases and Behavior Change
```{r}
# for reproducibility
set.seed(123)

#raw cases
quarantine_country_total_anova_figure <- ggstatsplot::ggbetweenstats(
  data = data_final,
  x = self_quarantine,
  y = confirmed_country,
  title = "Total Country Cases by Behavior Change",
  xlab = "Self Quarantine",
  ylab = "Reported Cases in Country",
  messages = FALSE,
  pairwise.comparisons = TRUE, # display significant pairwise comparisons
  pairwise.annotation = "p.value", # how do you want to annotate the pairwise comparisons
  p.adjust.method = "bonferroni") # method for adjusting p-values for multiple comparisons
# adding new components to `ggstatsplot` default
quarantine_country_total_anova_figure

#Log Transformed Cases
quarantine_country_total_anova_figure_log <- ggstatsplot::ggbetweenstats(
  data = data_final,
  x = self_quarantine,
  y = confirmed_country_log,
  title = "Total Country Cases by Behavior Change",
  xlab = "Self Quarantine",
  ylab = "Reported Cases in Country (Log Transformed)",
  messages = FALSE,
  pairwise.comparisons = TRUE, # display significant pairwise comparisons
  pairwise.annotation = "p.value", # how do you want to annotate the pairwise comparisons
  p.adjust.method = "bonferroni") # method for adjusting p-values for multiple comparisons
# adding new components to `ggstatsplot` default
quarantine_country_total_anova_figure_log

# Check for homogeneity of variance
leveneTest(confirmed_country_log ~ self_quarantine, center = mean, data = data_final)

# ANCOVA
quarantine_country_total_model_unadjusted <- lmer(self_quarantine_integer ~ confirmed_country_log + (1|country_region), data = drop_na(data_final,age,gender_cleaned),REML=FALSE, lmerControl(optimizer = "Nelder_Mead"))
summary(quarantine_country_total_model_unadjusted)
tab_model(quarantine_country_total_model_unadjusted)
#effectsize::cohens_f(quarantine_country_total_model_unadjusted)
sjstats::anova_stats(quarantine_country_total_model_unadjusted)
AIC(quarantine_country_total_model_unadjusted)
BIC(quarantine_country_total_model_unadjusted)


# Check residuals for normality
quarantine_country_total_model_residuals_unadjusted <- resid(quarantine_country_total_model_unadjusted)
shapiro.test(quarantine_country_total_model_residuals_unadjusted)


# Adjusted ANCOVA
quarantine_country_total_model_adjusted <- lmer(self_quarantine_integer ~ confirmed_country_log + age + gender_cleaned +  date + (1|country_region), data = drop_na(data_final,age,gender_cleaned), REML=FALSE, lmerControl(optimizer = "Nelder_Mead"))
tab_model(quarantine_country_total_model_adjusted)
#effectsize::cohens_f(quarantine_country_total_model)
sjstats::anova_stats(quarantine_country_total_model_adjusted)
AIC(quarantine_country_total_model_adjusted)
BIC(quarantine_country_total_model_adjusted)


# Check residuals for normality
quarantine_country_total_model_residuals_adjusted <- resid(quarantine_country_total_model_adjusted)
shapiro.test(quarantine_country_total_model_residuals_adjusted)

anova(quarantine_country_total_model_unadjusted,quarantine_country_total_model_adjusted)

tab_model(quarantine_country_total_model_unadjusted, quarantine_country_total_model_adjusted,
          pred.labels = c("Intercept", "Confirmed Cases Within Country", "Age", "Gender: Woman",  "Gender: Nonbinary","Gender: Prefer to Self Describe","Gender: Prefer not to Answer","Date"),
          dv.labels = c("Unadjusted Model: Self Quarantine", "Adjusted Model: Self Quarantine"),
          string.ci = "Conf. Int (95%)",
          string.p = "P-Value",show.icc=FALSE,show.r2=FALSE,show.se=TRUE,
          digits = 3,
          show.aic = TRUE,
          file = "~/Dropbox/COVID-19 Study/Tables/quarantine_TCC_table.doc")
```



#Analysis 4: Economic Impacts

##Lost Job and COVID Concern
```{r}
data_final$covid_concern_integer <- as.integer(data_final$covid_concern)

job_covid_anova_figure <- ggstatsplot::ggbetweenstats(
  data = data_final,
  x = job_lost,
  y = covid_concern_integer,
  title = "COVID Concern by Loss of Job",
  xlab = "Loss of Job",
  ylab = "COVID-19 Concern",
  messages = FALSE,
  pairwise.comparisons = TRUE, # display significant pairwise comparisons
  pairwise.annotation = "p.value", # how do you want to annotate the pairwise comparisons
  p.adjust.method = "bonferroni") # method for adjusting p-values for multiple comparisons
# adding new components to `ggstatsplot` default
job_covid_anova_figure


# Check for homogeneity of variance
leveneTest(covid_concern_integer ~ job_lost, center = mean, data = data_final)

# ANCOVA
job_covid_model_unadjusted <- lmer(covid_concern_integer ~ job_lost + (1|country_region) + date, data = drop_na(data_final,age,gender_cleaned),REML=FALSE)
summary(job_covid_model_unadjusted)
#effectsize::cohens_f(job_covid_model)
tab_model(job_covid_model_unadjusted)
sjstats::anova_stats(job_covid_model_unadjusted)
AIC(job_covid_model_unadjusted)
BIC(job_covid_model_unadjusted)


# Check residuals for normality
job_covid_model_residuals_unadjusted <- resid(job_covid_model_unadjusted)
shapiro.test(job_covid_model_residuals_unadjusted)


# ANCOVA
job_covid_model_adjusted <- lmer(covid_concern_integer ~ job_lost + age + gender_cleaned + (1|country_region) + date, data = drop_na(data_final,age,gender_cleaned),REML=FALSE)
summary(job_covid_model_adjusted)
#effectsize::cohens_f(job_covid_model)
tab_model(job_covid_model_adjusted)
sjstats::anova_stats(job_covid_model_adjusted)
AIC(job_covid_model_adjusted)
BIC(job_covid_model_adjusted)


# Check residuals for normality
job_covid_model_residuals_adjusted <- resid(job_covid_model_adjusted)
shapiro.test(job_covid_model_residuals_adjusted)

anova(job_covid_model_unadjusted,job_covid_model_adjusted)

tab_model(job_covid_model_unadjusted, job_covid_model_adjusted,
          pred.labels = c("Intercept", "Loss of Job", "Age", "Gender: Woman",  "Gender: Nonbinary","Gender: Prefer to Self Describe","Gender: Prefer not to Answer","Date"),
          dv.labels = c("Unadjusted Model: COVID-19 Concern", "Adjusted Model: COVID-19 Concern"),
          string.ci = "Conf. Int (95%)",
          string.p = "P-Value",show.icc=FALSE,show.r2=FALSE,show.se=TRUE,
          digits = 3,
          show.aic = TRUE,
          file = "~/Dropbox/COVID-19 Study/Tables/job_covid_table.doc")
```


##Lost Job and GAD
```{r}

job_gad_anova_figure <- ggstatsplot::ggbetweenstats(
  data = data_final,
  x = job_lost,
  y = gad_total,
  title = "GAD by Loss of Job",
  xlab = "Loss of Job",
  ylab = "GAD Score",
  messages = FALSE,
  pairwise.comparisons = TRUE, # display significant pairwise comparisons
  pairwise.annotation = "p.value", # how do you want to annotate the pairwise comparisons
  p.adjust.method = "bonferroni") # method for adjusting p-values for multiple comparisons
# adding new components to `ggstatsplot` default
job_gad_anova_figure


# Check for homogeneity of variance
leveneTest(gad_total ~ job_lost, center = mean, data = data_final)

# ANCOVA
job_gad_model_unadjusted <- lmer(gad_total ~ job_lost + (1|country_region), data = drop_na(data_final,age,gender_cleaned),REML=FALSE)
summary(job_gad_model_unadjusted)
#effectsize::cohens_f(job_gad_model)
tab_model(job_gad_model_unadjusted)
sjstats::anova_stats(job_gad_model_unadjusted)
AIC(job_gad_model_unadjusted)
BIC(job_gad_model_unadjusted)


# Check residuals for normality
job_gad_residuals_unadjusted <- resid(job_gad_model_unadjusted)
shapiro.test(job_gad_residuals_unadjusted)


# ANCOVA Adjusted
job_gad_model_adjusted <- lmer(gad_total ~ job_lost + age + gender_cleaned + date + (1|country_region), data = drop_na(data_final,age,gender_cleaned),REML=FALSE)
summary(job_gad_model_adjusted)
#effectsize::cohens_f(job_gad_model)
tab_model(job_gad_model_adjusted)
sjstats::anova_stats(job_gad_model_adjusted)
AIC(job_gad_model_adjusted)
BIC(job_gad_model_adjusted)


# Check residuals for normality
job_gad_residuals_adjusted <- resid(job_gad_model_adjusted)
shapiro.test(job_gad_residuals_adjusted)

anova(job_gad_model_unadjusted,job_gad_model_adjusted)

tab_model(job_gad_model_unadjusted, job_gad_model_adjusted,
          pred.labels = c("Intercept", "Loss of Job", "Age", "Gender: Woman",  "Gender: Nonbinary","Gender: Prefer to Self Describe","Gender: Prefer not to Answer","Date"),
          dv.labels = c("Unadjusted Model: GAD Scores", "Adjusted Model: GAD Scores"),
          string.ci = "Conf. Int (95%)",
          string.p = "P-Value",show.icc=FALSE,show.r2=FALSE,show.se=TRUE,
          digits = 3,
          show.aic = TRUE,
          file = "~/Dropbox/COVID-19 Study/Tables/job_gad_table.doc")
```

##Lost Job and PHQ
```{r}

job_phq_anova_figure <- ggstatsplot::ggbetweenstats(
  data = data_final,
  x = job_lost,
  y = phq_total,
  title = "PHQ by Loss of Job",
  xlab = "Loss of Job",
  ylab = "PHQ Score",
  messages = FALSE,
  pairwise.comparisons = TRUE, # display significant pairwise comparisons
  pairwise.annotation = "p.value", # how do you want to annotate the pairwise comparisons
  p.adjust.method = "bonferroni") # method for adjusting p-values for multiple comparisons
# adding new components to `ggstatsplot` default
job_phq_anova_figure


# Check for homogeneity of variance
leveneTest(phq_total ~ job_lost, center = mean, data = data_final)

# ANCOVA
job_phq_model_unadjusted <- lmer(phq_total ~ job_lost + date + (1|country_region), data = drop_na(data_final,age,gender_cleaned),REML=FALSE)
summary(job_phq_model_unadjusted)
#effectsize::cohens_f(job_covid_model)
tab_model(job_phq_model_unadjusted)
sjstats::anova_stats(job_phq_model_unadjusted)
AIC(job_phq_model_unadjusted)
BIC(job_phq_model_unadjusted)


# Check residuals for normality
job_phq_model_residuals_unadjusted <- resid(job_phq_model_unadjusted)
shapiro.test(job_phq_model_residuals_unadjusted)

# ANCOVA adjusted
job_phq_model_adjusted <- lmer(phq_total ~ job_lost +age + gender_cleaned +date + (1|country_region), data = drop_na(data_final,age,gender_cleaned))
summary(job_phq_model_adjusted)
#effectsize::cohens_f(job_covid_model)
tab_model(job_phq_model_adjusted)
sjstats::anova_stats(job_phq_model_adjusted)
AIC(job_phq_model_adjusted)
BIC(job_phq_model_adjusted)


# Check residuals for normality
job_covid_model_residuals_adjusted <- resid(job_phq_model_adjusted)
shapiro.test(job_covid_model_residuals_adjusted)

anova(job_phq_model_unadjusted,job_phq_model_adjusted)

tab_model(job_phq_model_unadjusted, job_phq_model_adjusted,
          pred.labels = c("Intercept", "Loss of Job", "Age", "Gender: Woman",  "Gender: Nonbinary","Gender: Prefer to Self Describe","Gender: Prefer not to Answer","Date"),
          dv.labels = c("Unadjusted Model: PHQ Scores", "Adjusted Model: PHQ Scores"),
          string.ci = "Conf. Int (95%)",
          string.p = "P-Value",show.icc=FALSE,show.r2=FALSE,show.se=TRUE,
          digits = 3,
          show.aic = TRUE,
          file = "~/Dropbox/COVID-19 Study/Tables/job_phq_table.doc")
```

##Income Lost and COVID Concern
```{r}

income_covid_anova_figure <- ggstatsplot::ggbetweenstats(
  data = data_final,
  x = income_lost,
  y = covid_concern_integer,
  title = "COVID Concern by Loss of Income",
  xlab = "Loss of Income",
  ylab = "COVID-19 Concern",
  messages = FALSE,
  pairwise.comparisons = TRUE, # display significant pairwise comparisons
  pairwise.annotation = "p.value", # how do you want to annotate the pairwise comparisons
  p.adjust.method = "bonferroni") # method for adjusting p-values for multiple comparisons
# adding new components to `ggstatsplot` default
income_covid_anova_figure


# Check for homogeneity of variance
leveneTest(covid_concern_integer ~ income_lost, center = mean, data = data_final)

# ANCOVA
income_covid_model_unadjusted <- lmer(covid_concern_integer ~ income_lost + (1|country_region) + date, data = drop_na(data_final,age,gender_cleaned), control = lmerControl(optimizer = "Nelder_Mead"))
summary(income_covid_model_unadjusted)
#effectsize::cohens_f(job_covid_model)
tab_model(income_covid_model_unadjusted)
sjstats::anova_stats(income_covid_model_unadjusted)
AIC(income_covid_model_unadjusted)
BIC(income_covid_model_unadjusted)


# Check residuals for normality
income_covid_model_residuals_unadjusted <- resid(income_covid_model_unadjusted)
shapiro.test(income_covid_model_residuals_unadjusted)



# ANCOVA
income_covid_model_adjusted <- lmer(covid_concern_integer ~ income_lost + age + gender_cleaned +(1|country_region) + date, data = drop_na(data_final,age,gender_cleaned), control = lmerControl(optimizer = "Nelder_Mead"))
summary(income_covid_model_adjusted)
#effectsize::cohens_f(job_covid_model)
tab_model(income_covid_model_adjusted)
sjstats::anova_stats(income_covid_model_adjusted)
AIC(income_covid_model_adjusted)
BIC(income_covid_model_adjusted)


# Check residuals for normality
income_covid_model_residuals_adjusted <- resid(income_covid_model_adjusted)
shapiro.test(income_covid_model_residuals_adjusted)

anova(income_covid_model_unadjusted,income_covid_model_adjusted)

tab_model(income_covid_model_unadjusted, income_covid_model_adjusted,
          pred.labels = c("Intercept", "Loss of Income", "Age", "Gender: Woman",  "Gender: Nonbinary","Gender: Prefer to Self Describe","Gender: Prefer not to Answer", "Date"),
          dv.labels = c("Unadjusted Model: COVID-19 Concern", "Adjusted Model: COVID-19 Concern"),
          string.ci = "Conf. Int (95%)",
          string.p = "P-Value",show.icc=FALSE,show.r2=FALSE,show.se=TRUE,
          digits = 3,
          show.aic = TRUE,
          file = "~/Dropbox/COVID-19 Study/Tables/income_covid_table.doc")
```

##Income Job and GAD
```{r}

income_gad_anova_figure <- ggstatsplot::ggbetweenstats(
  data = data_final,
  x = income_lost,
  y = gad_total,
  title = "GAD by Loss of Income",
  xlab = "Loss of Income",
  ylab = "GAD Score",
  messages = FALSE,
  pairwise.comparisons = TRUE, # display significant pairwise comparisons
  pairwise.annotation = "p.value", # how do you want to annotate the pairwise comparisons
  p.adjust.method = "bonferroni") # method for adjusting p-values for multiple comparisons
# adding new components to `ggstatsplot` default
income_gad_anova_figure


# Check for homogeneity of variance
leveneTest(gad_total ~ income_lost, center = mean, data = data_final)

# ANCOVA
income_gad_model_unadjusted <- lmer(gad_total ~ income_lost + (1|country_region), data = drop_na(data_final,age,gender_cleaned))
summary(income_gad_model_unadjusted)
#effectsize::cohens_f(income_gad_model)
tab_model(income_gad_model_unadjusted)
sjstats::anova_stats(income_gad_model_unadjusted)
AIC(income_gad_model_unadjusted)
BIC(income_gad_model_unadjusted)


# Check residuals for normality
income_gad_residuals_unadjusted <- resid(income_gad_model_unadjusted)
shapiro.test(income_gad_residuals_unadjusted)



# ANCOVA
income_gad_model_adjusted <- lmer(gad_total ~ income_lost + age + gender_cleaned + date + (1|country_region), data = drop_na(data_final,age,gender_cleaned))
summary(income_gad_model_adjusted)
#effectsize::cohens_f(income_gad_model)
tab_model(income_gad_model_adjusted)
sjstats::anova_stats(income_gad_model_adjusted)
AIC(income_gad_model_adjusted)
BIC(income_gad_model_adjusted)


# Check residuals for normality
income_gad_residuals_adjusted <- resid(income_gad_model_adjusted)
shapiro.test(income_gad_residuals_adjusted)

anova(income_gad_model_unadjusted,income_gad_model_adjusted)

tab_model(income_gad_model_unadjusted, income_gad_model_adjusted,
          pred.labels = c("Intercept", "Loss of Income", "Age", "Gender: Woman",  "Gender: Nonbinary","Gender: Prefer to Self Describe","Gender: Prefer not to Answer","Date"),
          dv.labels = c("Unadjusted Model: GAD Scores", "Adjusted Model: GAD Scores"),
          string.ci = "Conf. Int (95%)",
          string.p = "P-Value",show.icc=FALSE,show.r2=FALSE,show.se=TRUE,
          digits = 3,
          show.aic = TRUE,
          file = "~/Dropbox/COVID-19 Study/Tables/income_gad_table.doc")
```


##Lost Income and PHQ
```{r}

income_phq_anova_figure <- ggstatsplot::ggbetweenstats(
  data = data_final,
  x = income_lost,
  y = phq_total,
  title = "PHQ by Loss of Job",
  xlab = "Loss of Income",
  ylab = "PHQ Score",
  messages = FALSE,
  pairwise.comparisons = TRUE, # display significant pairwise comparisons
  pairwise.annotation = "p.value", # how do you want to annotate the pairwise comparisons
  p.adjust.method = "bonferroni") # method for adjusting p-values for multiple comparisons
# adding new components to `ggstatsplot` default
income_phq_anova_figure


# Check for homogeneity of variance
leveneTest(phq_total ~ income_lost, center = mean, data = data_final)

# ANCOVA
income_phq_model_unadjusted <- lmer(phq_total ~ income_lost + date + (1|country_region), data = drop_na(data_final,age,gender_cleaned))
summary(income_phq_model_unadjusted)
#effectsize::cohens_f(job_covid_model)
tab_model(income_phq_model_unadjusted)
sjstats::anova_stats(income_phq_model_unadjusted)
AIC(income_phq_model_unadjusted)
BIC(income_phq_model_unadjusted)


# Check residuals for normality
income_phq_model_residuals_unadjusted <- resid(income_phq_model_unadjusted)
shapiro.test(income_phq_model_residuals_unadjusted)


# ANCOVA
income_phq_model_adjusted <- lmer(phq_total ~ income_lost + age + gender_cleaned+ date + (1|country_region), data = drop_na(data_final,age,gender_cleaned))
summary(income_phq_model_adjusted)
#effectsize::cohens_f(job_covid_model)
tab_model(income_phq_model_adjusted)
sjstats::anova_stats(income_phq_model_adjusted)
AIC(income_phq_model_adjusted)
BIC(income_phq_model_adjusted)


# Check residuals for normality
income_phq_model_residuals_adjusted <- resid(income_phq_model_adjusted)
shapiro.test(income_phq_model_residuals_adjusted)

anova(income_phq_model_adjusted,income_phq_model_unadjusted)

tab_model(income_phq_model_unadjusted, income_phq_model_adjusted,
          pred.labels = c("Intercept", "Loss of Income", "Age", "Gender: Woman",  "Gender: Nonbinary","Gender: Prefer to Self Describe","Gender: Prefer not to Answer","Date"),
          dv.labels = c("Unadjusted Model: PHQ Scores", "Adjusted Model: PHQ Scores"),
          string.ci = "Conf. Int (95%)",
          string.p = "P-Value",show.icc=FALSE,show.r2=FALSE,show.se=TRUE,
          digits = 3,
          show.aic = TRUE,
          file = "~/Dropbox/COVID-19 Study/Tables/income_phq_table.doc")
```

#Deidentify Data
```{r}
data_osf <- data_final %>% 
  dplyr::select(response_id,
                date,
                gad_total,
                phq_total,
                covid_concern_integer,
                flu_sxs_personal,
               flu_sxs_other,
               covid_test,
               hospitalized,
               passed_away,
               lifestyle_changes,
               self_quarantine,
               job_lost,
               job_unable_work,
               income_lost,
               money_situation,
               food_security,
               gender_cleaned,
               race_cleaned,
               ethnicity_cleaned,
               education,
               income,
               age,
               political_orientation,
               occupation,
               recruitment_source,
               confirmed,
               deaths,
               recovered,
               deaths_country,
               recovered_country,
               deaths_world,
               recovered_world,
               state_diff_days,
               confirmed_country,
               country_diff_days,
               lockdown_date,
               confirmed_world,
               world_diff_days,
               days_since_lockdown,
               confirmed_log,
               confirmed_country_log,
               confirmed_world_log)

data.table::setDT(data_osf)
data_osf <- data_osf %>% 
    dplyr::select(-country_region, -province_state)

#Save Data

write.csv(data_osf, file = "~/Dropbox/COVID-19 Study/Data/deidentified_osf_data.csv")
```
